---
params:
  section: "abc"
  pg: "abc"
  var: "abc"
title: "`r paste0(params$section,': ',params$pg)`"
output: 
 html_document: 
   self_contained: no
   mathjax: null
   highlight: null
   fig_width: 10
   theme: null
   template: "../../CCO_template_html.html"
---

```{r, include=F}
knitr::opts_chunk$set(echo = F, warning=F,message = F) # Code is the same as 9-17_important_happiness document
```

<link rel="stylesheet" href="../../styles.css" type="text/css" />

```{r, child='W:/CCO-WORKING-FS/Projects/big ask survey/analysis/markdown/child docs/navigation_child_doc.rmd'}


```


## `r params$pg`

**% of respondents overall saying they are both worried about something and that they think its unlikely they will have a better life than their parents**

```{r, fig.width=10}

hap_col<-names(df)[grepl("id|worry_|parents_clean$|wt",names(df))]

df_imp<-df[!q4_parents_clean %in% dk_vals & !`q3_worry_I dont know` %in% c("Yes") & !`q3_worry_I dont want to say` %in% c("Yes")][,..hap_col]

hap_cols<-hap_col[grepl("worry",hap_col) & !grepl("dont|Other",hap_col)]

imp_cols<-hap_col[grepl("parents_clean",hap_col) & !grepl("dont want|wt",hap_col)]

corr_list<-rbindlist(lapply(hap_cols,function(x){
  
  col<-c("id",x,imp_cols,"wt")
  
  tb<-melt(df_imp[,..col
         ],id.vars=c("id",x,"wt"))[,(x):=ifelse(get(x) =="Yes",1,0)
                              ][,value:=ifelse(value %in% target_vals,1,0)
                                ][,.(c=sum(wt)),by=.(hap=get(x),variable,value)
                                  ][,perc:=c/sum(c),by=.(variable)
                                    ][hap==1 & value==1]
  
  tb$hap_var<-splitF(q_lookup_worry$label[q_lookup_worry$var==x])
  
  tb$variable<-plyr::mapvalues(tb$variable,q_lookup$var,sapply(q_lookup$label,splitF))
  
  tb
})
)

corr_list$perc<-ifelse(corr_list$perc<0.01,round(corr_list$perc,3)*100,
                       round(corr_list$perc,2)*100)

ggplot(corr_list,
       aes(x=reorder(hap_var,perc),y=perc,group=variable,fill=variable))+geom_col(colour="grey50",position = position_dodge(0.9))+geom_text(aes(label=paste0(perc,"%")),position = position_dodge(0.9),hjust=-0.1)+scale_y_continuous(limits=c(0,max(corr_list$perc,na.rm=T)*1.1))+
  theme(axis.text.x = element_text(angle=90),
        panel.grid=element_blank(),
        panel.background = element_blank(),
        axis.ticks=element_blank())+
  scale_fill_brewer(type="qual",palette=3, name="", guide=F)+coord_flip()+
  ylab("% of 9-17 yr olds\n")+xlab("")

```

**Correlation between what children are worried about and whether they think it is unlikely they will have a better life than their parents**

*Bars = % of children saying they are worried about each item that also think its unlikely they will have a better life than their parents*

```{r, fig.width=10}

hap_col<-names(df)[grepl("id|worry_|parents_clean$|wt",names(df))]

df_imp<-df[!q4_parents_clean %in% dk_vals][,..hap_col]

hap_cols<-hap_col[grepl("worry",hap_col) & !grepl("dont|Other",hap_col)]

imp_cols<-hap_col[grepl("parents_clean",hap_col) & !grepl("dont want|wt",hap_col)]

corr_list<-rbindlist(lapply(hap_cols,function(x){
  
  col<-c("id",x,imp_cols,"wt")
  
  tb<-melt(df_imp[,..col
         ],id.vars=c("id",x,"wt"))[,(x):=ifelse(get(x) =="Yes",1,0)
                              ][,value:=ifelse(value %in% target_vals,1,0)
                                ][,.(c=sum(wt)),by=.(hap=get(x),variable,value)
                                  ][,perc:=c/sum(c),by=.(hap,variable)
                                    ][hap==1 & value==1]
  
  tb$hap_var<-splitF(q_lookup_worry$label[q_lookup_worry$var==x])
  
  tb$variable<-plyr::mapvalues(tb$variable,q_lookup$var,sapply(q_lookup$label,splitF))
  
  tb
})
)

ggplot(corr_list,
       aes(x=reorder(hap_var,perc),y=perc*100,group=variable,fill=variable))+geom_col(colour="grey50",position = position_dodge(0.9))+geom_text(aes(label=paste0(round(perc,2)*100,"%")),position = position_dodge(0.9),hjust=-0.5)+
  theme(axis.text.x = element_text(angle=90),
        panel.grid=element_blank(),
        panel.background = element_blank(),
        axis.ticks=element_blank())+
  scale_fill_brewer(type="qual",palette=3, name="", guide=F)+coord_flip()+
  ylab("%\n")+xlab("")

```

