---
title: "What do children think is important for their future?"
output: 
 html_document: 
   self_contained: no
   mathjax: null
   highlight: null
   css: styles.css
   fig_width: 10
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning=F,message = F)

require(readxl)
require(data.table)
require(dplyr)
require(ggplot2)
require(reactable)
require(htmltools)
require(tippy)

stem<-"W:/CCO-WORKING-FS/Projects/big ask survey/analysis/survey data/cleaned data/"

target_vals<-"Yes"

dk_vals<-""

col1<-"% of children that think x is important..."

search_str<-"important_"

table_f<-function(x,df_use=df){
  
  x<-unlist(strsplit(x,"[|]"))
  
  reg<-paste0("^",x,"$")
  
  reg_string<-paste0("^id$|important_|wt|",paste0(reg,collapse="|"))
  hap_col<-names(df_use)[grepl(reg_string,names(df_use))]
  
  hap_col<-hap_col[!grepl("dont",hap_col)]
  
df_la<-melt(df_use[,..hap_col],id.vars = c("id",x,"wt"))[,variable:=plyr::mapvalues(variable,
                                                                                    q_lookup$var,
                                                                                    q_lookup$label)]

df_la[,value:=ifelse(value %in% target_vals,1,0)
           ]
}

source("W:/CCO-WORKING-FS/Projects/big ask survey/analysis/scripts/markdown_functions.R",local=knitr::knit_global())
  
```

```{r}

df<-readRDS("W:/CCO-WORKING-FS/Projects/big ask survey/analysis/survey data/final data/6-8_weighted.rds")


imd<-fread(file="W:/CCO-WORKING-FS/Projects/big ask survey/analysis/aux data/imd2019lsoa.csv")[Measurement=="Decile"][,Value:=ceiling(Value/2)]

df<-df[!dfe_phase %in% "Secondary"
       ][,id:=paste0(id,survey)
         ][,dem_gender_clean:=plyr::mapvalues(dem_gender_clean,
                                              c("Boy","Girl"),c("Male","Female"))
           ][,any_mh:=ifelse(`dem_support_A healthcare worker`=="Yes","Yes","No")
             ][`q3_important_I dont want to say` %in% c(NA,"No") &
                 `q3_important_I dont know` %in% c(NA,"No") &
                 `q3_important_I dont know what will be important` %in% c(NA,"No")]

q_lookup<-fread("W:\\CCO-WORKING-FS\\Projects\\big ask survey\\analysis\\aux data\\6-8_important_q_lookup.csv")


q_lookup_hap<-fread("W:\\CCO-WORKING-FS\\Projects\\big ask survey\\analysis\\aux data\\6-8_happy_q_lookup.csv")

age_grp<-"6-8"


 reg_string<-"^id$|feel.*_"
 
 hap_col<-names(df)[grepl(reg_string,names(df))]

  
df_feel<-melt(df[,..hap_col],id.vars = c("id"))[,variable:=gsub("^.*_","",variable)]

df_feel<-df_feel[,value:=ifelse(value %in% dk_vals,NA,
                        ifelse(value %in% "Yes",1,0))
           ][,any_neg:=ifelse(variable %in% c("Stressed","Lonely","Worried","Sad"),1,0)
             ][,any_pos:=ifelse(variable %in% c("Happy","Safe","Calm","Energetic","Excited"),1,0)
               ][,any_bored:=ifelse(variable=="Bored",1,0)]

df_sent<-df_feel[value==1][,lapply(.SD,function(x){
  ifelse(sum(x)>0,1,0)
  }),by=.(id),.SDcols=c("any_neg","any_pos","any_bored")]

df<-merge(df,df_sent)

```


<a href="index.html">Return to home page</a>

<script src="extra_js.js"></script>

## Results {.tabset}

### Summary

<h3>Key stats</h3>
<div class="stat-boxes">

<div class="col-xs-12 col-sm-6 col-lg-3">
<div class="stat">
<div class="stat-box-outer">
<div class="stat-box-inner">
<p class="figure">Key stat</p>
</div>
</div>
</div>
</div>

<div class="col-xs-12 col-sm-6 col-lg-3">
<div class="stat">
<div class="stat-box-outer">
<div class="stat-box-inner">
<p class="figure">Key stat</p>
</div>
</div>
</div>
</div>

<div class="col-xs-12 col-sm-6 col-lg-3">
<div class="stat">
<div class="stat-box-outer">
<div class="stat-box-inner">
<p class="figure">Key stat</p>
</div>
</div>
</div>
</div>

<div class="col-xs-12 col-sm-6 col-lg-3">
<div class="stat">
<div class="stat-box-outer">
<div class="stat-box-inner">
<p class="figure">Key stat</p>
</div>
</div>
</div>
</div>

</div>

<div class="row"></div>



<h3>About this data</h3>

INTRO TEXT

### Overall rates

<h3>What do children think is important for their future></h3>

```{r}
dat<-table_f("")[,.(c=sum(wt)),by=.(variable,value)][,perc:=round(c/sum(c),2)*100,by=.(variable)][value==1][,.(variable,perc)]

ggplot(dat,
       aes(x=reorder(variable,perc),y=perc))+
  geom_col(fill="light blue",colour="grey20")+coord_flip()+geom_text(aes(label=paste0(perc,"%")),hjust=1)+
  theme_bw()+xlab("")+ylab("% of 9-17 yr olds")

```

### Combinations of items

<h3>What combinations of items do children think are important?</h3>

```{r, fig.width=10}

hap_col<-c(q_lookup$var,"id","wt")

dat<-df[,..hap_col
        ]

q_vars<-hap_col[grepl("^q",hap_col)]

dat<-dat[,(q_vars):=lapply(.SD,function(x){
  ifelse(x %in% dk_vals,NA,
                        ifelse(x %in% target_vals,1,0))
           
}),.SDcols=q_vars]

vars_comb<-names(dat)[!grepl("id|wt|Other",names(dat))]

two_way<-as.data.table(gtools::combinations(length(vars_comb),2,vars_comb))

names(two_way)<-c("var1","var2")

two_way_out<-rbindlist(lapply(seq_len(nrow(two_way)),function(x){
  
  v1<-two_way$var1[x]
  v2<-two_way$var2[x]
  
  lb1<-q_lookup$label[q_lookup$var==v1]
  lb2<-q_lookup$label[q_lookup$var==v2]
  
  dat[,.(c=sum(wt)),by=.(var1=get(v1),var2=get(v2))
  ][,`:=`(perc=round(c/sum(c),2)*100,base=sum(c))
  ][var1==1 & var2==1
    ][,l2_4:=NULL
      ][,comb:=paste0(v1,"-",v2)
        ][,`:=`(v1=lb1,v2=lb2)][,.(comb,c,perc,base,v1,v2)]
  
  
})
)[,`:=`(v1=factor(sapply(v1,splitF),levels=sapply(q_lookup$label,splitF)),
        v2=factor(sapply(v2,splitF),levels=sapply(q_lookup$label,splitF))
        )]

pal<-RColorBrewer::brewer.pal(7,"Reds")



ggplot(two_way_out,
       aes(x=v2,y=v1,v1,fill=perc))+geom_tile(colour="grey50")+
  geom_text(aes(label=paste0(round(perc,1),"%")))+
  theme(axis.text.x = element_text(angle=90),
        panel.grid=element_blank(),
        panel.background = element_blank(),
        axis.ticks=element_blank())+
  scale_fill_gradient(low=pal[1],high=pal[length(pal)],name="% of respondents")+
  ylab("")+xlab("")



```

<h3>Which combinations are most correlated?</h3>

*Note: red = stronger positive correlation (i.e. children selecting row are more likely to also select column in the chart below), blue = stronger negative correlation*

```{r,fig.width=10}

dat<-df[,..hap_col
        ]

q_vars<-hap_col[grepl("^q",hap_col)]

dat<-dat[,(q_vars):=lapply(.SD,function(x){
  ifelse(x %in% dk_vals,NA,
                        ifelse(x %in% target_vals,1,0))
           
}),.SDcols=q_vars]

vars_comb<-names(dat)[!grepl("id|wt|Other",names(dat))]

two_way<-as.data.table(gtools::combinations(length(vars_comb),2,vars_comb))

names(two_way)<-c("var1","var2")

two_way<-two_way[!grepl("dont",var1) & ! grepl("dont",var2)]

two_way_out<-rbindlist(lapply(seq_len(nrow(two_way)),function(x){
  
  v1<-two_way$var1[x]
  v2<-two_way$var2[x]
  
  lb1<-q_lookup$label[q_lookup$var==v1]
  lb2<-q_lookup$label[q_lookup$var==v2]
  
  tb<-dat[,.(c=sum(wt)),by=.(var1=get(v1),var2=get(v2))
  ]
  
  grid<-expand.grid(var1=unique(tb$var1),var2=unique(tb$var2))
  
  tb<-merge(tb,grid,all.y=T)[,c:=ifelse(is.na(c),0,c)][,`:=`(perc=c/sum(c),base=sum(c)),by=.(var1)
  ][var2==1]
  
   tb<-dcast(tb[,.(var2,perc,var1)],var2~var1,value.var="perc"
            )[,rr:=`1`/`0`][,comb:=paste0(v1,"-",v2)
        ][,`:=`(v1=lb1,v2=lb2)][,.(comb,rr,v1,v2)]
   
})

)[,`:=`(v1=factor(sapply(v1,splitF),levels=sapply(q_lookup$label,splitF)),
        v2=factor(sapply(v2,splitF),levels=sapply(q_lookup$label,splitF))
        )]

pal_div<-RColorBrewer::brewer.pal(7,"RdBu")


ggplot(two_way_out,
       aes(x=v2,y=v1,v1,fill=rr))+geom_tile(colour="grey50")+
  theme(axis.text.x = element_text(angle=90),
        panel.grid=element_blank(),
        panel.background = element_blank(),
        axis.ticks=element_blank())+
  scale_fill_gradient2(low=pal_div[length(pal_div)],high=pal_div[1],midpoint=1,name="Relative risk\n(Children selecting row \nare x times more\nlikely to also say\ncolumn)")+
  ylab("")+xlab("")





```

### Local area rates

<h3>How is this different in different areas?</h3>

```{r,child='W:\\CCO-WORKING-FS\\Projects\\big ask survey\\analysis\\markdown\\child docs\\map_child_doc.rmd'}

```

### Local area chars

<h3>How is this different based on an area's characteristics?</h3>

```{r,child='W:\\CCO-WORKING-FS\\Projects\\big ask survey\\analysis\\markdown\\child docs\\area_chars_child_doc.rmd'}

```

### Child demographics

<h3>How is this different by children's characteristics?</h3>

```{r,child='W:\\CCO-WORKING-FS\\Projects\\big ask survey\\analysis\\markdown\\child docs\\child_chars_child_doc.rmd'}

```

### Vulnearble children

<h3>How is this different for disadvantaged/vulnerable children?</h3>

```{r,child='W:\\CCO-WORKING-FS\\Projects\\big ask survey\\analysis\\markdown\\child docs\\disad_child_doc.rmd'}

```

### School chars

<h3>How is this different by where children go to school?</h3>

```{r,child='W:\\CCO-WORKING-FS\\Projects\\big ask survey\\analysis\\markdown\\child docs\\school_child_doc.rmd'}

```

### Link to happiness now

<h3>How is this different based on what they are unhappy about now?</h3>

*% of respondents overall that are unhappy with something and think something is important*

```{r, fig.width=10}
hap_col<-names(df)[grepl("id|happy.*_clean|important_|wt",names(df))]

df_imp<-df[,..hap_col]

hap_cols<-hap_col[grepl("happy",hap_col)]

imp_cols<-hap_col[grepl("imp",hap_col) & !grepl("dont|wt",hap_col)]


corr_list<-rbindlist(lapply(hap_cols,function(x){
  
  col<-c("id",x,imp_cols,"wt")
  
  tb<-melt(df_imp[,..col
         ],id.vars=c("id",x,"wt"))[,(x):=ifelse(get(x) %in% c("dont know","I dont know"),NA,
                                           ifelse(get(x) %in% c("Unhappy","Very unhappy","sad"),1,0))
                              ][,value:=ifelse(value=="Yes",1,0)
                                ][,.(c=sum(wt)),by=.(hap=get(x),variable,value)
                                  ][,perc:=c/sum(c),by=.(variable)
                                    ][hap==1 & value==1]
  
  tb$hap_var<-splitF(q_lookup_hap$label[q_lookup_hap$var==x])
  
  tb$variable<-plyr::mapvalues(tb$variable,q_lookup$var,sapply(q_lookup$label,splitF))
  
  tb
})
)

ggplot(corr_list,
       aes(x=variable,y=hap_var,fill=perc*100))+geom_tile(colour="grey50")+geom_text(aes(label=paste0(round(perc,3)*100,"%")))+
  theme(axis.text.x = element_text(angle=90),
        panel.grid=element_blank(),
        panel.background = element_blank(),
        axis.ticks=element_blank())+
  scale_fill_gradient(low=pal[1],high=pal[length(pal)],name="% of respondents saying both")+
  ylab("Children are unhappy with...")+xlab("Children think x is important...")

```

*Correlations between what children are unhappy with and what they they think is important*

*Note: red = stronger positive correlation (i.e. children selecting row are more likely to also select column in the chart below), blue = stronger negative correlation*

```{r, fig.width=10}

hap_col<-names(df)[grepl("id|happy.*_clean|important_|wt",names(df))]

df_imp<-df[,..hap_col]

hap_cols<-hap_col[grepl("happy",hap_col)]

imp_cols<-hap_col[grepl("imp",hap_col) & !grepl("dont|wt|Other",hap_col)]

corr_list<-rbindlist(lapply(hap_cols,function(x){
  
  col<-c("id",x,imp_cols,"wt")
  
  tb<-melt(df_imp[,..col
         ],id.vars=c("id",x,"wt"))[,(x):=ifelse(get(x) %in% c("dont know","I dont know"),NA,
                                           ifelse(get(x) %in% c("Unhappy","Very unhappy","sad"),1,0))
                              ][!is.na(get(x)) & !is.na(value)][,value:=ifelse(value=="Yes",1,0)
                                ][,.(c=sum(wt)),by=.(hap=get(x),variable,value)
                                  ][,perc:=c/sum(c),by=.(hap,variable)
                                    ]
  
  tb<-dcast(tb[value==1][,.(variable,perc,hap)],variable~hap,value.var="perc"
            )[,rr:=`1`/`0`][,.(variable,rr)]
  
  
  tb$hap_var<-splitF(q_lookup_hap$label[q_lookup_hap$var==x])
  
  tb$variable<-plyr::mapvalues(tb$variable,q_lookup$var,sapply(q_lookup$label,splitF))
  
  tb
})
)

pal_div<-RColorBrewer::brewer.pal(7,"RdBu")

ggplot(corr_list,
       aes(x=variable,y=hap_var,fill=rr))+geom_tile(colour="grey50")+
  theme(axis.text.x = element_text(angle=90),
        panel.grid=element_blank(),
        panel.background = element_blank(),
        axis.ticks=element_blank())+
  scale_fill_gradient2(low=pal_div[length(pal_div)],high=pal_div[1],midpoint=1,name="Relative risk\n(Children unhappy with row\nare x times more\nlikely to think\ncolumn is important)")+
  ylab("Children are unhappy with...")+xlab("Children think x is important...")


```

```{r, fig.width=10}
hap_col<-names(df)[grepl("id|any_(pos|neg|bored)|important_|wt",names(df))]

df_imp<-df[,..hap_col]

hap_cols<-hap_col[grepl("any_(pos|neg|bored)",hap_col)]

imp_cols<-hap_col[grepl("imp",hap_col) & !grepl("dont|wt|Other",hap_col)]


corr_list<-rbindlist(lapply(hap_cols,function(x){
  
  col<-c("id",x,imp_cols,"wt")
  
  tb<-melt(df_imp[,..col
         ],id.vars=c("id",x,"wt"))[,value:=ifelse(value=="Yes",1,0)
                                ][,.(c=sum(wt)),by=.(hap=get(x),variable,value)
                                  ][,perc:=c/sum(c),by=.(variable)
                                    ][hap==1 & value==1]
  
  tb$hap_var<-plyr::mapvalues(x,c("any_pos","any_neg","any_bored"),
                               c("Any positive","Any negative","Any bored"))
  
  tb$variable<-plyr::mapvalues(tb$variable,q_lookup$var,sapply(q_lookup$label,splitF))
  
  tb
})
)

ggplot(corr_list,
       aes(x=variable,y=hap_var,fill=perc*100))+geom_tile(colour="grey50")+geom_text(aes(label=paste0(round(perc,2)*100,"%")))+
  theme(axis.text.x = element_text(angle=90),
        panel.grid=element_blank(),
        panel.background = element_blank(),
        axis.ticks=element_blank())+
  scale_fill_gradient(low=pal[1],high=pal[length(pal)],name="% of respondents saying both")+
  ylab("Children feel...")+xlab("Children think x is important...")

```

```{r}
corr_list<-rbindlist(lapply(hap_cols,function(x){
  
  col<-c("id",x,imp_cols,"wt")
  
  tb<-melt(df_imp[,..col
         ],id.vars=c("id",x,"wt"))[!is.na(get(x)) & !is.na(value)][,value:=ifelse(value=="Yes",1,0)
                                ][,.(c=sum(wt)),by=.(hap=get(x),variable,value)
                                  ][,perc:=c/sum(c),by=.(hap,variable)
                                    ]
  
  tb<-dcast(tb[value==1][,.(variable,perc,hap)],variable~hap,value.var="perc"
            )[,rr:=`1`/`0`][,.(variable,rr)]
  
  
   tb$hap_var<-plyr::mapvalues(x,c("any_pos","any_neg","any_bored"),
                               c("Any positive","Any negative","Any bored"))
  
  tb$variable<-plyr::mapvalues(tb$variable,q_lookup$var,sapply(q_lookup$label,splitF))
  
  
  tb
})
)

pal_div<-RColorBrewer::brewer.pal(7,"RdBu")

ggplot(corr_list,
       aes(x=variable,y=hap_var,fill=rr))+geom_tile(colour="grey50")+
  theme(axis.text.x = element_text(angle=90),
        panel.grid=element_blank(),
        panel.background = element_blank(),
        axis.ticks=element_blank())+
  scale_fill_gradient2(low=pal_div[length(pal_div)],high=pal_div[1],midpoint=1,name="Relative risk\n(Children unhappy with row\nare x times more\nlikely to feel\ncolumn)")+
  ylab("Children are unhappy with...")+xlab("Children feel...")
```

