---
title: "Do children think they will have a better life than their parents?"
output: 
 html_document:
   self_contained: no
   mathjax: null
   highlight: null
   css: styles.css
   fig_width: 10
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning=F,message = F)

require(readxl)
require(data.table)
require(dplyr)
require(ggplot2)
require(reactable)
require(htmltools)
require(tippy)

age_grp<-NULL

stem<-"W:/CCO-WORKING-FS/Projects/big ask survey/analysis/survey data/cleaned data/"

dk_vals<-c("I dont know","I dont want to say","Other","I am not sure")

search_str<-"parents_clean"

target_vals<-c("Very unlikely","Unlikely","Fairly unlikely","Yes")

col1<-"%"

table_f<-function(x,df_use=df){
  
  x<-unlist(strsplit(x,"[|]"))
  
  reg<-paste0("^",x,"$")
  
  reg_string<-paste0("^id$|parents_clean|wt|",paste0(reg,collapse="|"))
  hap_col<-names(df_use)[grepl(reg_string,names(df_use))]
  
  hap_col<-hap_col[!grepl("dont want to",hap_col)]
  
  df_la<-melt(df_use[!q4_parents_clean %in% dk_vals][,..hap_col],id.vars = c("id",x,"wt"))[,variable:=plyr::mapvalues(variable,
                                                                                                                            q_lookup$var,
                                                                                                                            q_lookup$label)]
  
  df_la[,value:=ifelse(value %in% target_vals,1,0)
  ]
}

source("W:/CCO-WORKING-FS/Projects/big ask survey/analysis/scripts/markdown_functions.R",local=knitr::knit_global())

pal<-RColorBrewer::brewer.pal(7,"Reds")

```

```{r}

df<-readRDS("W:/CCO-WORKING-FS/Projects/big ask survey/analysis/survey data/final data/13-17_weighted.rds")

imd<-fread(file="W:/CCO-WORKING-FS/Projects/big ask survey/analysis/aux data/imd2019lsoa.csv")[Measurement=="Decile"][,Value:=ceiling(Value/2)]

df<-df[,id:=paste0(id,survey)
       ][!q4_parents_clean %in% dk_vals
         ][,q4_parents_clean_2:=ifelse(!q4_parents_clean %in% c("Fairly likely","Very likely","Likely"),"Yes","No")]

q_lookup<-data.table(var=c("q4_parents_clean","q4_parents_clean_2"),label=c("Children think its unlikely they will have a better life than their parents","Children think its likely they will have a better life than their parents"))

q_lookup_hap<-fread("W:\\CCO-WORKING-FS\\Projects\\big ask survey\\analysis\\aux data\\13-17_happy_q_lookup.csv")
q_lookup_hap$var<-gsub("Option ","q1_happy_",q_lookup_hap$var)

q_lookup_imp<-fread("W:\\CCO-WORKING-FS\\Projects\\big ask survey\\analysis\\aux data\\13-17_important_q_lookup.csv")
q_lookup<-q_lookup[!grepl("dont want",var)]

q_lookup_worry<-fread("W:\\CCO-WORKING-FS\\Projects\\big ask survey\\analysis\\aux data\\13-17_worry_q_lookup.csv")
q_lookup_worry<-q_lookup_worry[!grepl("dont want",var)]

```


<a href="index.html">Return to home page</a>

<script src="extra_js.js"></script>

## Results {.tabset}

### Summary

<h3>Key stats</h3>
<div class="stat-boxes">

<div class="col-xs-12 col-sm-6 col-lg-3">
<div class="stat">
<div class="stat-box-outer">
<div class="stat-box-inner">
<p class="figure">Key stat</p>
</div>
</div>
</div>
</div>

<div class="col-xs-12 col-sm-6 col-lg-3">
<div class="stat">
<div class="stat-box-outer">
<div class="stat-box-inner">
<p class="figure">Key stat</p>
</div>
</div>
</div>
</div>

<div class="col-xs-12 col-sm-6 col-lg-3">
<div class="stat">
<div class="stat-box-outer">
<div class="stat-box-inner">
<p class="figure">Key stat</p>
</div>
</div>
</div>
</div>

<div class="col-xs-12 col-sm-6 col-lg-3">
<div class="stat">
<div class="stat-box-outer">
<div class="stat-box-inner">
<p class="figure">Key stat</p>
</div>
</div>
</div>
</div>

</div>


<h3> About this data</h3>

INTRO TEXT

### Overall rates

<h3>% of children saying it is likely/unlikely that they will have a better life than their parents</h3>

```{r}
dat<-df[!q4_parents_clean %in% dk_vals
        ][,q4_parents_clean:=ifelse(q4_parents_clean %in% dk_vals,NA,
                                    ifelse(q4_parents_clean %in% c("Fairly likely","Very likely","Likely"),"Likely",
                                           ifelse(q4_parents_clean %in% target_vals,"Unlikely","Neither likely/unlikely")))
  ][,.(c=sum(wt)),by=.(q4_parents_clean)][,perc:=round(c/sum(c),2)*100,]

ggplot(dat,
       aes(x=reorder(q4_parents_clean,perc),y=perc))+
  geom_col(fill="light blue",colour="grey20")+coord_flip()+geom_text(aes(label=paste0(perc,"%")),hjust=1)+
  theme_bw()+xlab("How likely ist it you will have\na better life than your parents?\n")+ylab("% of 9-17 yr olds")

```

### Local area rates

<h3>How is this different in different areas?</h3>

```{r,child='W:\\CCO-WORKING-FS\\Projects\\big ask survey\\analysis\\markdown\\child docs\\map_child_doc.rmd'}

```

### Local area chars

<h3>How is this different based on an area's characteristics?</h3>

```{r,child='W:\\CCO-WORKING-FS\\Projects\\big ask survey\\analysis\\markdown\\child docs\\area_chars_child_doc.rmd'}

```

### Child Demographics

<h3>How is this different by children's characteristics?</h3>

```{r,child='W:\\CCO-WORKING-FS\\Projects\\big ask survey\\analysis\\markdown\\child docs\\child_chars_child_doc.rmd'}

```

### Link to Disadvantage

<h3>How is this different for disadvantaged/vulnerable children?</h3>

```{r,child='W:\\CCO-WORKING-FS\\Projects\\big ask survey\\analysis\\markdown\\child docs\\disad_child_doc.rmd'}

```

### School chars

<h3>How is this different by where children go to school?</h3>

```{r,child='W:\\CCO-WORKING-FS\\Projects\\big ask survey\\analysis\\markdown\\child docs\\school_child_doc.rmd'}

```

### Link to current happiness

<h3>How is this different based on what they are unhappy about now?</h3>

*% of respondents overall saying they are unhappy with something and that they think its unlikely they will have a better life than their parents*


```{r, fig.width=10, include=F}

hap_col<-names(df)[grepl("id|happy.*_clean|parents_clean$|wt",names(df))]

df_imp<-df[!q4_parents_clean %in% dk_vals][,..hap_col]

hap_cols<-hap_col[grepl("happy",hap_col)]

imp_cols<-hap_col[grepl("parents",hap_col) & !grepl("dont want|wt",hap_col)]

corr_list<-rbindlist(lapply(hap_cols,function(x){
  
  col<-c("id",x,imp_cols,"wt")
  
  tb<-melt(df_imp[,..col
         ],id.vars=c("id",x,"wt"))[,(x):=ifelse(get(x) %in% c("dont know","I dont know"),NA,
                                           ifelse(get(x) %in% c("Unhappy","Very unhappy","sad"),1,0))
                              ][,value:=ifelse(value %in% target_vals,1,0)][,.(c=sum(wt)),by=.(hap=get(x),variable,value)
                                  ][,perc:=c/sum(c),by=.(variable)
                                    ][hap==1 & value==1]
  
  tb$hap_var<-splitF(q_lookup_hap$label[q_lookup_hap$var==x])
  
  tb$variable<-plyr::mapvalues(tb$variable,q_lookup$var,sapply(q_lookup$label,splitF))
  
  tb
})
)

ggplot(corr_list,
       aes(x=reorder(hap_var,perc),y=perc*100,group=variable,fill=variable))+geom_col(colour="grey50",position = position_dodge(0.9))+geom_text(aes(label=paste0(round(perc,2)*100,"%")),position = position_dodge(0.9),hjust=-0.1)+scale_y_continuous(limits=c(0,max(corr_list$perc*100,na.rm=T)*1.1))+scale_y_continuous(limits=c(0,max(corr_list$perc*100,na.rm=T)*1.1))+
  theme(axis.text.x = element_text(angle=90),
        panel.grid=element_blank(),
        panel.background = element_blank(),
        axis.ticks=element_blank())+
  scale_fill_brewer(type="qual",palette=3, name="", guide=F)+coord_flip()+
  ylab("% of repondents saying they think its\nunlikely they will have\na better life than their parents\nand x\n")+xlab("")

```

*Correlation between what children are unhappy about and whether they think it is unlikely they will have a better life than their parents*

*Bars = % of children saying they are unhappy with each item that think its unlikely they will have a better life than their parents*

```{r, fig.width=10}

hap_col<-names(df)[grepl("id|happy.*_clean|parents_clean$|wt",names(df))]

df_imp<-df[!q4_parents_clean %in% dk_vals][,..hap_col]

hap_cols<-hap_col[grepl("happy",hap_col)]

imp_cols<-hap_col[grepl("parents_clean",hap_col) & !grepl("dont want|wt",hap_col)]

corr_list<-rbindlist(lapply(hap_cols,function(x){
  
  col<-c("id",x,imp_cols,"wt")
  
  tb<-melt(df_imp[,..col
         ],id.vars=c("id",x,"wt"))[,(x):=ifelse(get(x) %in% c("dont know","I dont know"),NA,
                                           ifelse(get(x) %in% c("Unhappy","Very unhappy","sad"),1,0))
                              ][,value:=ifelse(value %in% target_vals,1,0)
                                ][,.(c=sum(wt)),by=.(hap=get(x),variable,value)
                                  ][,perc:=c/sum(c),by=.(hap,variable)
                                    ][hap==1 & value==1]
  
  tb$hap_var<-splitF(q_lookup_hap$label[q_lookup_hap$var==x])
  
  tb$variable<-plyr::mapvalues(tb$variable,q_lookup$var,sapply(q_lookup$label,splitF))
  
  tb
})
)

ggplot(corr_list,
       aes(x=reorder(hap_var,perc),y=perc*100,group=variable,fill=variable))+geom_col(colour="grey50",position = position_dodge(0.9))+geom_text(aes(label=paste0(round(perc,2)*100,"%")),position = position_dodge(0.9),hjust=-0.1)+scale_y_continuous(limits=c(0,max(corr_list$perc*100,na.rm=T)*1.1))+
  theme(axis.text.x = element_text(angle=90),
        panel.grid=element_blank(),
        panel.background = element_blank(),
        axis.ticks=element_blank())+
  scale_fill_brewer(type="qual",palette=3, name="", guide=F)+coord_flip()+
  ylab("%\n")+xlab("")

```

### Link to importance for future

<h3>How is this different based on what they think is important for the future?</h3>

*% of respondents overall saying both that something is important for their future and that they think its unlikely they will have a better life than their parents*


```{r, fig.width=10, include=F}

hap_col<-names(df)[grepl("id|important_|parents_clean$|wt",names(df))]

df_imp<-df[!q4_parents_clean %in% dk_vals][,..hap_col]

hap_cols<-hap_col[grepl("important",hap_col) & !grepl("dont",hap_col)]

imp_cols<-hap_col[grepl("parents_clean",hap_col) & !grepl("dont want|wt",hap_col)]

corr_list<-rbindlist(lapply(hap_cols,function(x){
  
  col<-c("id",x,imp_cols,"wt")
  
  tb<-melt(df_imp[,..col
         ],id.vars=c("id",x,"wt"))[,(x):=ifelse(get(x) =="Yes",1,0)
                              ][,value:=ifelse(value %in% target_vals,1,0)
                                ][,.(c=sum(wt)),by=.(hap=get(x),variable,value)
                                  ][,perc:=c/sum(c),by=.(variable)
                                    ][hap==1 & value==1]
  
  tb$hap_var<-splitF(q_lookup_imp$label[q_lookup_imp$var==x])
  
  tb$variable<-plyr::mapvalues(tb$variable,q_lookup$var,sapply(q_lookup$label,splitF))
  
  tb
})
)

ggplot(corr_list,
       aes(x=reorder(hap_var,perc),y=perc*100,group=variable,fill=variable))+geom_col(colour="grey50",position = position_dodge(0.9))+geom_text(aes(label=paste0(round(perc,2)*100,"%")),position = position_dodge(0.9),hjust=-0.1)+scale_y_continuous(limits=c(0,max(corr_list$perc*100,na.rm=T)*1.1))+
  theme(axis.text.x = element_text(angle=90),
        panel.grid=element_blank(),
        panel.background = element_blank(),
        axis.ticks=element_blank())+
  scale_fill_brewer(type="qual",palette=3, name="", guide=F)+coord_flip()+
  ylab("%\n")+xlab("")

```

*Correlation between what children think is important and whether they think it is unlikely they will have a better life than their parents*

*Bars = % of children saying they think an item is important that think its unlikely they will have a better life than their parents*

```{r, fig.width=10}

hap_col<-names(df)[grepl("id|important_|parents_clean$|wt",names(df))]

df_imp<-df[!q4_parents_clean %in% dk_vals][,..hap_col]

hap_cols<-hap_col[grepl("important",hap_col) & !grepl("dont",hap_col)]

imp_cols<-hap_col[grepl("parents_clean",hap_col) & !grepl("dont want|wt",hap_col)]

corr_list<-rbindlist(lapply(hap_cols,function(x){
  
  col<-c("id",x,imp_cols,"wt")
  
  tb<-melt(df_imp[,..col
         ],id.vars=c("id",x,"wt"))[,(x):=ifelse(get(x) =="Yes",1,0)
                              ][,value:=ifelse(value %in% target_vals,1,0)
                                ][,.(c=sum(wt)),by=.(hap=get(x),variable,value)
                                  ][,perc:=c/sum(c),by=.(hap,variable)
                                    ][hap==1 & value==1]
  
  tb$hap_var<-splitF(q_lookup_imp$label[q_lookup_imp$var==x])
  
  tb$variable<-plyr::mapvalues(tb$variable,q_lookup$var,sapply(q_lookup$label,splitF))
  
  tb
})
)

ggplot(corr_list,
       aes(x=reorder(hap_var,perc),y=perc*100,group=variable,fill=variable))+geom_col(colour="grey50",position = position_dodge(0.9))+geom_text(aes(label=paste0(round(perc,2)*100,"%")),position = position_dodge(0.9),hjust=-0.1)+scale_y_continuous(limits=c(0,max(corr_list$perc*100,na.rm=T)*1.1))+
  theme(axis.text.x = element_text(angle=90),
        panel.grid=element_blank(),
        panel.background = element_blank(),
        axis.ticks=element_blank())+
  scale_fill_brewer(type="qual",palette=3, name="", guide=F)+coord_flip()+
  ylab("%\n")+xlab("")

```

### Link to future worries

<h3>How is this different based on what they worry about in the future?</h3>

*% of respondents overall saying they are both worried about something and that they think its unlikely they will have a better life than their parents*

```{r, fig.width=10, include=F}

hap_col<-names(df)[grepl("id|worry_|parents_clean$|wt",names(df))]

df_imp<-df[!q4_parents_clean %in% dk_vals][,..hap_col]

hap_cols<-hap_col[grepl("worry",hap_col) & !grepl("dont",hap_col)]

imp_cols<-hap_col[grepl("parents_clean",hap_col) & !grepl("dont want|wt",hap_col)]

corr_list<-rbindlist(lapply(hap_cols,function(x){
  
  col<-c("id",x,imp_cols,"wt")
  
  tb<-melt(df_imp[,..col
         ],id.vars=c("id",x,"wt"))[,(x):=ifelse(get(x) =="Yes",1,0)
                              ][,value:=ifelse(value %in% target_vals,1,0)
                                ][,.(c=sum(wt)),by=.(hap=get(x),variable,value)
                                  ][,perc:=c/sum(c),by=.(variable)
                                    ][hap==1 & value==1]
  
  tb$hap_var<-splitF(q_lookup_imp$label[q_lookup_imp$var==x])
  
  tb$variable<-plyr::mapvalues(tb$variable,q_lookup$var,sapply(q_lookup$label,splitF))
  
  tb
})
)

ggplot(corr_list,
       aes(x=reorder(hap_var,perc),y=perc*100,group=variable,fill=variable))+geom_col(colour="grey50",position = position_dodge(0.9))+geom_text(aes(label=paste0(round(perc,2)*100,"%")),position = position_dodge(0.9),hjust=-0.1)+scale_y_continuous(limits=c(0,max(corr_list$perc*100,na.rm=T)*1.1))+
  theme(axis.text.x = element_text(angle=90),
        panel.grid=element_blank(),
        panel.background = element_blank(),
        axis.ticks=element_blank())+
  scale_fill_brewer(type="qual",palette=3, name="", guide=F)+coord_flip()+
  ylab("%\n")+xlab("")

```

*Correlation between what children are worried about and whether they think it is unlikely they will have a better life than their parents*

*Bars = % of children saying they are worried about each item that also think its unlikely they will have a better life than their parents*

```{r, fig.width=10}

hap_col<-names(df)[grepl("id|worry_|parents_clean$|wt",names(df))]

df_imp<-df[!q4_parents_clean %in% dk_vals][,..hap_col]

hap_cols<-hap_col[grepl("worry",hap_col) & !grepl("dont",hap_col)]

imp_cols<-hap_col[grepl("parents_clean",hap_col) & !grepl("dont want|wt",hap_col)]

corr_list<-rbindlist(lapply(hap_cols,function(x){
  
  col<-c("id",x,imp_cols,"wt")
  
  tb<-melt(df_imp[,..col
         ],id.vars=c("id",x,"wt"))[,(x):=ifelse(get(x) =="Yes",1,0)
                              ][,value:=ifelse(value %in% target_vals,1,0)
                                ][,.(c=sum(wt)),by=.(hap=get(x),variable,value)
                                  ][,perc:=c/sum(c),by=.(hap,variable)
                                    ][hap==1 & value==1]
  
  tb$hap_var<-splitF(q_lookup_worry$label[q_lookup_worry$var==x])
  
  tb$variable<-plyr::mapvalues(tb$variable,q_lookup$var,sapply(q_lookup$label,splitF))
  
  tb
})
)

ggplot(corr_list,
       aes(x=reorder(hap_var,perc),y=perc*100,group=variable,fill=variable))+geom_col(colour="grey50",position = position_dodge(0.9))+geom_text(aes(label=paste0(round(perc,2)*100,"%")),position = position_dodge(0.9),hjust=-0.5)+
  theme(axis.text.x = element_text(angle=90),
        panel.grid=element_blank(),
        panel.background = element_blank(),
        axis.ticks=element_blank())+
  scale_fill_brewer(type="qual",palette=3, name="", guide=F)+coord_flip()+
  ylab("%\n")+xlab("")

```

### Regressions

<h3>What factors are most predictive of children not expecting a better life than their parents?</h3>

```{r, child='W:\\CCO-WORKING-FS\\Projects\\big ask survey\\analysis\\markdown\\child docs\\regression_child_doc.rmd'}

```