---
title: "How happy are children with their life currently?"
output: 
 html_document: 
   self_contained: no
   mathjax: null
   highlight: null
   css: styles.css
   fig_width: 10
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning=F,message = F)

require(readxl)
require(data.table)
require(dplyr)
require(ggplot2)
require(reactable)
require(htmltools)
require(tippy)

age_grp<-NULL

stem<-"W:/CCO-WORKING-FS/Projects/big ask survey/analysis/survey data/cleaned data/"

search_str<-"happy.*clean"

dk_vals<-c("I don't know","Not applicable","dont know","I dont want to say")

target_vals<-c("Unhappy","Very unhappy","sad")


table_f<-function(x,df_use=df){
  
  x<-unlist(strsplit(x,"[|]"))
  
  reg<-paste0("^",x,"$")
  
  reg_string<-paste0("^id$|happy.*clean|^wt$|",paste0(reg,collapse="|"))
  hap_col<-names(df_use)[grepl(reg_string,names(df_use))]

  
df_la<-melt(df_use[,..hap_col],id.vars = c("id",x,"wt"))[,variable:=plyr::mapvalues(variable,
                                                                                    q_lookup$var,
                                                                                    q_lookup$label)]

df_la[,value:=ifelse(value %in% dk_vals,NA,
                        ifelse(value %in% target_vals,1,0))
           ]
}

source("W:/CCO-WORKING-FS/Projects/big ask survey/analysis/scripts/markdown_functions.R",local=knitr::knit_global())
  
col1<-"% of children unhappy with..."

```

```{r}

df<-readRDS("W:/CCO-WORKING-FS/Projects/big ask survey/analysis/survey data/final data/9-17_weighted.rds")

imd<-fread(file="W:/CCO-WORKING-FS/Projects/big ask survey/analysis/aux data/imd2019lsoa.csv")[Measurement=="Decile"][,Value:=ceiling(Value/2)]

df<-df[,id:=paste0(id,survey)
       ][,bme:=ifelse(dem_eth_grp=="White",1,0)
         ]

q_lookup<-fread("W:\\CCO-WORKING-FS\\Projects\\big ask survey\\analysis\\aux data\\13-17_happy_q_lookup.csv")
q_lookup$var<-gsub("Option ","q1_happy_",q_lookup$var)

q_lookup_clust<-fread("W:\\CCO-WORKING-FS\\Projects\\big ask survey\\analysis\\aux data\\13-17_happy_cluster_q_lookup.csv")

```


<a href="index.html">Return to home page</a>

<script src="extra_js.js"></script>

## Results {.tabset}

### Summary

<h3>Key stats</h3>
<div class="stat-boxes">

<div class="col-xs-12 col-sm-6 col-lg-3">
<div class="stat">
<div class="stat-box-outer">
<div class="stat-box-inner">
<p class="figure">Key stat</p>
</div>
</div>
</div>
</div>

<div class="col-xs-12 col-sm-6 col-lg-3">
<div class="stat">
<div class="stat-box-outer">
<div class="stat-box-inner">
<p class="figure">Key stat</p>
</div>
</div>
</div>
</div>

<div class="col-xs-12 col-sm-6 col-lg-3">
<div class="stat">
<div class="stat-box-outer">
<div class="stat-box-inner">
<p class="figure">Key stat</p>
</div>
</div>
</div>
</div>

<div class="col-xs-12 col-sm-6 col-lg-3">
<div class="stat">
<div class="stat-box-outer">
<div class="stat-box-inner">
<p class="figure">Key stat</p>
</div>
</div>
</div>
</div>

</div>

<h3>About this data</h3>

INTRO TEXT

### Overall rates

<h3>How happy are children overall?</h3>

```{r,fig.width=8,fig.height=8}
hap_col<-names(df)[grepl("^id$|happy.*_clean|^wt$",names(df))]

df_happy<-melt(df[,..hap_col],id.vars = c("id","wt"))

dat<-copy(df_happy)[,value:=ifelse(value %in% dk_vals,NA,
                        ifelse(value %in% target_vals,"Unhappy",
                               ifelse(value %in% c("Neither happy nor unhappy (neutral)","neural"),"Neutral","Happy")))
           ][!is.na(value)][,.(c=sum(wt)),by=.(variable,value)][,perc:=round(c/sum(c),2)*100,by=.(variable)][,.(variable,perc,value)]

dat<-merge(dat,q_lookup,by.x="variable",by.y="var")

pal_div<-RColorBrewer::brewer.pal(7,"RdBu")


ggplot(dat,
       aes(x=reorder(label,perc),y=perc,group=value,fill=value))+
  geom_col(colour="grey20",position = position_dodge(0.9))+coord_flip()+geom_text(aes(label=paste0(perc,"%")),hjust=ifelse(dat$perc<10,-0.1,1),position = position_dodge(0.9))+
  scale_fill_brewer(type="qual",palette=4,direction=-1,name="")+ylab("% of 9-17 yr olds")+xlab("")+
  theme_bw()

```


<h3>How many aspects of their lives are children unhappy with?</h3>

```{r}

df_happy<-melt(df[,..hap_col],id.vars = c("id","wt"))

dat<-copy(df_happy)[,value:=ifelse(value %in% dk_vals,NA,
                        ifelse(value %in% target_vals,1,0))
           ][!is.na(value)
             ][,.(tot=sum(value,na.rm=T)),by=.(id,wt)]

tb<-dat[][,.(c=sum(wt)),by=.(tot)
    ][,perc:=c/sum(c)][order(-tot)
                       ][,cum_perc:=cumsum(perc)
                         ][,cum_perc:=round(ifelse(tot==0,perc,cum_perc),3)*100
                           ][,tot:=ifelse(tot==0,"0",ifelse(tot==max(tot),"All",paste0(tot,"+")))
                             ][,.(tot,cum_perc)
                               ]

names(tb)<-c("Number of aspects of their life children are unhappy with","% of respondents")

reactable(tb,
             columns=list(`Number of aspects of their life children are unhappy with`=colDef(),`% of respondents`=colDef()),
    pagination = F,
    fullWidth = T,
    bordered = T,
    resizable = T,
    searchable = F,
    showSortable = T,
    language = reactableLang(searchPlaceholder = "Search table...",searchLabel = ""))

```

### Combinations of items

<h3>What combinations of things are children unhappy about?</h3>

```{r, child='W:\\CCO-WORKING-FS\\Projects\\big ask survey\\analysis\\markdown\\child docs\\combs_child_doc.rmd'}


```

### Local area rates

<h3>How are rates different in different areas?</h3>

```{r,child='W:\\CCO-WORKING-FS\\Projects\\big ask survey\\analysis\\markdown\\child docs\\map_child_doc.rmd'}

```

### Local area chars

<h3>How are rates different based on an area's characteristics?</h3>

```{r,child='W:\\CCO-WORKING-FS\\Projects\\big ask survey\\analysis\\markdown\\child docs\\area_chars_child_doc.rmd'}


```

### Child demographics

<h3>How are rates different by children's characteristics?</h3>

```{r,child='W:\\CCO-WORKING-FS\\Projects\\big ask survey\\analysis\\markdown\\child docs\\child_chars_child_doc.rmd'}

```

### Link to Disadvantage

<h3>How is this different for disadvantaged/vulnerable children?</h3>

```{r,child='W:\\CCO-WORKING-FS\\Projects\\big ask survey\\analysis\\markdown\\child docs\\disad_child_doc.rmd'}

```

### School chars

<h3>How is this different by where children go to school?</h3>

```{r,child='W:\\CCO-WORKING-FS\\Projects\\big ask survey\\analysis\\markdown\\child docs\\school_child_doc.rmd'}


```

### Regression

<h3>What factors are most predictive of children being unhappy?</h3>

```{r, child='W:\\CCO-WORKING-FS\\Projects\\big ask survey\\analysis\\markdown\\child docs\\regression_child_doc.rmd'}

```


### Segmentation

<h3>Can we combine children into groups that are unhappy about similar aspects of their life?</h3>

```{r, include=F}
mod<-"happy"
```


```{r, child='W:\\CCO-WORKING-FS\\Projects\\big ask survey\\analysis\\markdown\\child docs\\segmentation_child_doc.rmd'}

```

