---
title: "What do children worry about for their future?"
output: 
 html_document: 
   self_contained: no
   mathjax: null
   highlight: null
   css: styles.css
   fig_width: 10
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning=F,message = F)

require(readxl)
require(data.table)
require(dplyr)
require(ggplot2)
require(reactable)
require(htmltools)
require(tippy)

age_grp<-NULL

stem<-"W:/CCO-WORKING-FS/Projects/big ask survey/analysis/survey data/cleaned data/"

target_vals<-"Yes"

dk_vals<-""

search_str<-"worry_"

col1<-"% of children that are worried about x..."

table_f<-function(x,df_use=df){
  
  x<-unlist(strsplit(x,"[|]"))
  
  reg<-paste0("^",x,"$")
  
  reg_string<-paste0("^id$|worry_|^wt$|",paste0(reg,collapse="|"))
  hap_col<-names(df_use)[grepl(reg_string,names(df_use))]
  
  hap_col<-hap_col[!grepl("dont want to",hap_col)]
  
df_la<-melt(df_use[`q3_worry_I dont want to say` %in% c(NA,"No")][,..hap_col],id.vars = c("id",x,"wt"))[,variable:=plyr::mapvalues(variable,
                                                                                    q_lookup$var,
                                                                                    q_lookup$label)]

df_la[,value:=ifelse(value %in% target_vals,1,0)
           ]
}

source("W:/CCO-WORKING-FS/Projects/big ask survey/analysis/scripts/markdown_functions.R",local=knitr::knit_global())
```

```{r}

df<-readRDS("W:/CCO-WORKING-FS/Projects/big ask survey/analysis/survey data/final data/9-17_weighted.rds")

imd<-fread(file="W:/CCO-WORKING-FS/Projects/big ask survey/analysis/aux data/imd2019lsoa.csv")[Measurement=="Decile"][,Value:=ceiling(Value/2)]

df<-df[`q3_worry_I dont want to say` %in% c(NA,"No")]

q_lookup<-fread("W:\\CCO-WORKING-FS\\Projects\\big ask survey\\analysis\\aux data\\13-17_worry_q_lookup.csv")
q_lookup<-q_lookup[!grepl("dont want",var)]

q_lookup_hap<-fread("W:\\CCO-WORKING-FS\\Projects\\big ask survey\\analysis\\aux data\\13-17_happy_q_lookup.csv")
q_lookup_hap$var<-gsub("Option ","q1_happy_",q_lookup_hap$var)

q_lookup_imp<-fread("W:\\CCO-WORKING-FS\\Projects\\big ask survey\\analysis\\aux data\\13-17_important_q_lookup.csv")
q_lookup<-q_lookup[!grepl("dont want",var)]

hap_col<-names(df)[grepl("^id$|worry_|^wt$",names(df))]

q_lookup_clust<-fread("W:\\CCO-WORKING-FS\\Projects\\big ask survey\\analysis\\aux data\\13-17_happy_cluster_q_lookup.csv")


```


<a href="index.html">Return to home page</a>

<script src="extra_js.js"></script>

## Results {.tabset}

### Summary

<h3>Key stats
<div class="stat-boxes">

<div class="col-xs-12 col-sm-6 col-lg-3">
<div class="stat">
<div class="stat-box-outer">
<div class="stat-box-inner">
<p class="figure">Key stat</p>
</div>
</div>
</div>
</div>

<div class="col-xs-12 col-sm-6 col-lg-3">
<div class="stat">
<div class="stat-box-outer">
<div class="stat-box-inner">
<p class="figure">Key stat</p>
</div>
</div>
</div>
</div>

<div class="col-xs-12 col-sm-6 col-lg-3">
<div class="stat">
<div class="stat-box-outer">
<div class="stat-box-inner">
<p class="figure">Key stat</p>
</div>
</div>
</div>
</div>

<div class="col-xs-12 col-sm-6 col-lg-3">
<div class="stat">
<div class="stat-box-outer">
<div class="stat-box-inner">
<p class="figure">Key stat</p>
</div>
</div>
</div>
</div>

</div>

<div class="row"></div>



<h3>About this data

INTRO TEXT

### Overall rates

<h3>% of children reporting they are worried different things will not be true in 10 years</h3>

```{r}
dat<-table_f("")[!grepl("dont|Other",variable)][,.(c=sum(wt)),by=.(variable,value)][,perc:=round(c/sum(c),2)*100,by=.(variable)][value==1][,.(variable,perc)]

ggplot(dat,
       aes(x=reorder(variable,perc),y=perc))+
  geom_col(fill="light blue",colour="grey20")+coord_flip()+geom_text(aes(label=paste0(perc,"%")),hjust=1)+
  theme_bw()+xlab("")+ylab("% of 9-17 yr olds")

```

### Combinations of items

<h3>What combinations of items are children worried about?</h3>

```{r,child='W:\\CCO-WORKING-FS\\Projects\\big ask survey\\analysis\\markdown\\child docs\\combs_child_doc.rmd'}

```

### Local area rates

<h3>How is this different in different areas?</h3>

```{r,child='W:\\CCO-WORKING-FS\\Projects\\big ask survey\\analysis\\markdown\\child docs\\map_child_doc.rmd'}

```

### Local area chars

<h3>How is this different based on an area's characteristics?</h3>

```{r,child='W:\\CCO-WORKING-FS\\Projects\\big ask survey\\analysis\\markdown\\child docs\\area_chars_child_doc.rmd'}

```

### Child demographics

<h3>How is this different by children's characteristics?</h3>

```{r,child='W:\\CCO-WORKING-FS\\Projects\\big ask survey\\analysis\\markdown\\child docs\\child_chars_child_doc.rmd'}

```

### Link to Disadvantage

<h3>How is this different for disadvantaged/vulnerable children?</h3>

```{r,child='W:\\CCO-WORKING-FS\\Projects\\big ask survey\\analysis\\markdown\\child docs\\disad_child_doc.rmd'}

```

### School chars

<h3>How is this different by where children go to school?</h3>

```{r,child='W:\\CCO-WORKING-FS\\Projects\\big ask survey\\analysis\\markdown\\child docs\\school_child_doc.rmd'}

```

### Link to happiness now

<h3>How is this different based on what they are unhappy about now?</h3>

*% of respondents saying they are unhappy with something and that they are worried about*

```{r, fig.width=10}

hap_col<-names(df)[grepl("id|happy.*_clean|worry_|wt",names(df))]

pal<-RColorBrewer::brewer.pal(7,"Reds")

df_imp<-df[`q3_worry_I dont want to say` %in% c(NA,"No")][,..hap_col]

hap_cols<-hap_col[grepl("happy",hap_col)]

imp_cols<-hap_col[grepl("worry",hap_col) & !grepl("dont want|wt|Other",hap_col)]

corr_list<-rbindlist(lapply(hap_cols,function(x){
  
  col<-c("id",x,imp_cols,"wt")
  
  tb<-melt(df_imp[,..col
         ],id.vars=c("id",x,"wt"))[,(x):=ifelse(get(x) %in% c("dont know","I dont know"),NA,
                                           ifelse(get(x) %in% c("Unhappy","Very unhappy","sad"),1,0))
                              ][,value:=ifelse(value=="Yes",1,0)
                                ][,.(c=sum(wt)),by=.(hap=get(x),variable,value)
                                  ][,perc:=c/sum(c),by=.(variable)
                                    ][hap==1 & value==1]
  
  tb$hap_var<-splitF(q_lookup_hap$label[q_lookup_hap$var==x])
  
  tb$variable<-plyr::mapvalues(tb$variable,q_lookup$var,sapply(q_lookup$label,splitF))
  
  tb
})
)

corr_list$hap_var<-factor(corr_list$hap_var,
                          levels= sapply(q_lookup_hap$label,splitF))

corr_list$variable<-factor(corr_list$variable,
                          levels= sapply(q_lookup$label,splitF))


ggplot(corr_list,
       aes(x=variable,y=hap_var,fill=perc*100))+geom_tile(colour="grey50")+geom_text(aes(label=paste0(round(perc,2)*100,"%")))+
  theme(axis.text.x = element_text(angle=90),
        panel.grid=element_blank(),
        panel.background = element_blank(),
        axis.ticks=element_blank())+
  scale_fill_gradient(low=pal[1],high=pal[length(pal)],name="% of respondents saying both")+
  ylab("Children are unhappy with...")+xlab("Children are worried about...")

```

*Correlations between what children are unhappy with and what they are worried about*

*Note: red = stronger positive correlation (i.e. children selecting row are more likely to also select column in the chart below), blue = stronger negative correlation*

```{r, fig.width=10}

hap_col<-names(df)[grepl("id|happy.*_clean|worry_|wt",names(df))]

df_imp<-df[`q3_worry_I dont want to say` %in% c(NA,"No")][,..hap_col]

hap_cols<-hap_col[grepl("happy",hap_col)]

imp_cols<-hap_col[grepl("worry",hap_col) & !grepl("dont|Other|worried",hap_col)]

corr_list<-rbindlist(lapply(hap_cols,function(x){
  
  col<-c("id",x,imp_cols,"wt")
  
  tb<-melt(df_imp[,..col
         ],id.vars=c("id",x,"wt"))[,(x):=ifelse(get(x) %in% c("dont know","I dont know"),NA,
                                           ifelse(get(x) %in% c("Unhappy","Very unhappy","sad"),1,0))
                              ][!is.na(get(x)) & !is.na(value)][,value:=ifelse(value=="Yes",1,0)
                                ][,.(c=sum(wt)),by=.(hap=get(x),variable,value)
                                  ][,perc:=c/sum(c),by=.(hap,variable)
                                    ]
  
  tb<-dcast(tb[value==1][,.(variable,perc,hap)],variable~hap,value.var="perc"
            )[,rr:=`1`/`0`][,.(variable,rr)]
  
  
  tb$hap_var<-splitF(q_lookup_hap$label[q_lookup_hap$var==x])
  
  tb$variable<-plyr::mapvalues(tb$variable,q_lookup$var,sapply(q_lookup$label,splitF))
  
  tb
})
)

corr_list$hap_var<-factor(corr_list$hap_var,
                          levels= sapply(q_lookup_hap$label,splitF))

corr_list$variable<-factor(corr_list$variable,
                          levels= sapply(q_lookup$label,splitF))

pal_div<-RColorBrewer::brewer.pal(7,"RdBu")

ggplot(corr_list,
       aes(x=variable,y=hap_var,fill=rr))+geom_tile(colour="grey50")+
  geom_text(aes(label=round(rr,2)))+
  theme(axis.text.x = element_text(angle=90),
        panel.grid=element_blank(),
        panel.background = element_blank(),
        axis.ticks=element_blank())+
  scale_fill_gradient2(low=pal_div[length(pal_div)],high=pal_div[1],midpoint=1,name="Relative risk\n(Children unhappy with row\nare x times more\nlikely to be worried about\ncolumn)")+
  ylab("Children are unhappy with...")+xlab("Children are worried about...")

```

### Link to importance for future

<h3>How is this different based on what they think is important for the future?</h3>

*% of respondents saying they think something is important and they are worried about*

```{r, fig.width=10}

hap_col<-names(df)[grepl("id|important_|worry_|wt",names(df))]

df_imp<-df[`q3_worry_I dont want to say` %in% c(NA,"No")][,..hap_col]

hap_cols<-hap_col[grepl("important",hap_col) & !grepl("dont|Other",hap_col)]

imp_cols<-hap_col[grepl("worry",hap_col) & !grepl("dont want|Other|wt",hap_col)]

corr_list<-rbindlist(lapply(hap_cols,function(x){
  
  col<-c("id",x,imp_cols,"wt")
  
  tb<-melt(df_imp[,..col
         ],id.vars=c("id",x,"wt"))[,(x):=ifelse(get(x) =="Yes",1,0)
                              ][,value:=ifelse(value=="Yes",1,0)
                                ][,.(c=sum(wt)),by=.(hap=get(x),variable,value)
                                  ][,perc:=c/sum(c),by=.(variable)
                                    ][hap==1 & value==1]
  
  tb$hap_var<-splitF(q_lookup_imp$label[q_lookup_imp$var==x])
  
  tb$variable<-plyr::mapvalues(tb$variable,q_lookup$var,sapply(q_lookup$label,splitF))
  
  tb
})
)

corr_list$hap_var<-factor(corr_list$hap_var,
                          levels= sapply(q_lookup_imp$label,splitF))

corr_list$variable<-factor(corr_list$variable,
                          levels= sapply(q_lookup$label,splitF))

ggplot(corr_list,
       aes(x=variable,y=hap_var,fill=perc*100))+geom_tile(colour="grey50")+geom_text(aes(label=paste0(round(perc,2)*100,"%")))+
  theme(axis.text.x = element_text(angle=90),
        panel.grid=element_blank(),
        panel.background = element_blank(),
        axis.ticks=element_blank())+
  scale_fill_gradient(low=pal[1],high=pal[length(pal)],name="% of respondents selecting both")+
  ylab("Children think x is important...")+xlab("Children are worried about...")

```

*Correlations between what children think is important and what they are worried about*

*Note: red = stronger positive correlation (i.e. children selecting row are more likely to also select column in the chart below), blue = stronger negative correlation*

```{r, fig.width=10}

hap_col<-names(df)[grepl("id|important_|worry_|wt",names(df))]

df_imp<-df[`q3_worry_I dont want to say` %in% c(NA,"No")][,..hap_col]

hap_cols<-hap_col[grepl("important",hap_col) & !grepl("dont|Other",hap_col)]

imp_cols<-hap_col[grepl("worry",hap_col) & !grepl("dont|Other|worried|wt",hap_col)]

corr_list<-rbindlist(lapply(hap_cols,function(x){
  
  col<-c("id",x,imp_cols,"wt")
  
  tb<-melt(df_imp[,..col
         ],id.vars=c("id",x,"wt"))[,(x):=ifelse(get(x) =="Yes",1,0)
                              ][,value:=ifelse(value=="Yes",1,0)
                                ][,.(c=sum(wt)),by=.(hap=get(x),variable,value)
                                  ][,perc:=c/sum(c),by=.(hap,variable)
                                    ]
  
  tb<-dcast(tb[value==1][,.(variable,perc,hap)],variable~hap,value.var="perc"
            )[,rr:=`1`/`0`][,.(variable,rr)]
  
  tb$hap_var<-splitF(q_lookup_imp$label[q_lookup_imp$var==x])
  
  tb$variable<-plyr::mapvalues(tb$variable,q_lookup$var,sapply(q_lookup$label,splitF))
  
  tb
})
)

corr_list$hap_var<-factor(corr_list$hap_var,levels=sapply(q_lookup_imp$label,splitF))
corr_list$variable<-factor(corr_list$variable,levels=sapply(q_lookup$label,splitF))


ggplot(corr_list,
       aes(x=variable,y=hap_var,fill=rr))+geom_tile(colour="grey50")+
  geom_text(aes(label=round(rr,2)))+
  theme(axis.text.x = element_text(angle=90),
        panel.grid=element_blank(),
        panel.background = element_blank(),
        axis.ticks=element_blank())+
  scale_fill_gradient2(low=pal_div[length(pal_div)],high=pal_div[1],midpoint=1,name="Relative risk\n(Children think row is importnat\nare x times more\nlikely to be worried about\ncolumn)")+
  ylab("Children think x is important...")+xlab("Children are worried about...")

```

### Regressions

<h3>What factors are most predictive of what children worry about?</h3>

```{r, child='W:\\CCO-WORKING-FS\\Projects\\big ask survey\\analysis\\markdown\\child docs\\regression_child_doc.rmd'}

```

### Segmentation

<h3>Can we combine children into groups that are worried about similar things for their future?</h3>

```{r, include=F}
mod<-"worry"
```


```{r, child='W:\\CCO-WORKING-FS\\Projects\\big ask survey\\analysis\\markdown\\child docs\\segmentation_child_doc.rmd'}

```