---
params:
  section: "abc"
  pg: "abc"
  var: "abc"
title: "`r paste0(params$section,': ',params$pg)`"
output: 
 html_document: 
   self_contained: no
   mathjax: null
   highlight: null
   fig_width: 10
   theme: null
   template: "../../CCO_template_html.html"
---

```{r, include=F}
knitr::opts_chunk$set(echo = F, warning=F,message = F)
```

<link rel="stylesheet" href="../../styles.css" type="text/css" />

```{r, child='W:/CCO-WORKING-FS/Projects/big ask survey/analysis/markdown/child docs/navigation_child_doc.rmd'}


```

### Link to happiness now

<h3>How is this different based on what they are unhappy about now?</h3>

*% of respondents overall that are unhappy with something and think something is important*

```{r, fig.width=10}
hap_col<-names(df)[grepl("id|happy.*_clean|important_|wt",names(df))]

df_imp<-df[,..hap_col]

hap_cols<-hap_col[grepl("happy",hap_col)]

imp_cols<-hap_col[grepl("imp",hap_col) & !grepl("dont|wt",hap_col)]


corr_list<-rbindlist(lapply(hap_cols,function(x){
  
  col<-c("id",x,imp_cols,"wt")
  
  tb<-melt(df_imp[,..col
         ],id.vars=c("id",x,"wt"))[,(x):=ifelse(get(x) %in% c("dont know","I dont know"),NA,
                                           ifelse(get(x) %in% c("Unhappy","Very unhappy","sad","unhappy"),1,0))
                              ][,value:=ifelse(value=="Yes",1,0)
                                ][,.(c=sum(wt)),by=.(hap=get(x),variable,value)
                                  ][,perc:=c/sum(c),by=.(variable)
                                    ][hap==1 & value==1]
  
  tb$hap_var<-splitF(q_lookup_hap$label[q_lookup_hap$var==x])
  
  tb$variable<-plyr::mapvalues(tb$variable,q_lookup$var,sapply(q_lookup$label,splitF))
  
  tb
})
)

ggplot(corr_list,
       aes(x=variable,y=hap_var,fill=perc*100))+geom_tile(colour="grey50")+geom_text(aes(label=paste0(round(perc,3)*100,"%")))+
  theme(axis.text.x = element_text(angle=90),
        panel.grid=element_blank(),
        panel.background = element_blank(),
        axis.ticks=element_blank())+
  scale_fill_gradient(low=pal[1],high=pal[length(pal)],name="% of respondents saying both")+
  ylab("Children are unhappy with...")+xlab("Children think x is important...")

```

*Correlations between what children are unhappy with and what they they think is important*

*Note: red = stronger positive correlation (i.e. children selecting row are more likely to also select column in the chart below), blue = stronger negative correlation*

```{r, fig.width=10}

hap_col<-names(df)[grepl("id|happy.*_clean|important_|wt",names(df))]

df_imp<-df[,..hap_col]

hap_cols<-hap_col[grepl("happy",hap_col)]

imp_cols<-hap_col[grepl("imp",hap_col) & !grepl("dont|wt|Other",hap_col)]

corr_list<-rbindlist(lapply(hap_cols,function(x){
  
  col<-c("id",x,imp_cols,"wt")
  
  tb<-melt(df_imp[,..col
         ],id.vars=c("id",x,"wt"))[,(x):=ifelse(get(x) %in% c("dont know","I dont know"),NA,
                                           ifelse(get(x) %in% c("Unhappy","Very unhappy","sad","unhappy"),1,0))
                              ][!is.na(get(x)) & !is.na(value)][,value:=ifelse(value=="Yes",1,0)
                                ][,.(c=sum(wt)),by=.(hap=get(x),variable,value)
                                  ][,perc:=c/sum(c),by=.(hap,variable)
                                    ]
  
  tb<-dcast(tb[value==1][,.(variable,perc,hap)],variable~hap,value.var="perc"
            )[,rr:=`1`/`0`][,.(variable,rr)]
  
  
  tb$hap_var<-splitF(q_lookup_hap$label[q_lookup_hap$var==x])
  
  tb$variable<-plyr::mapvalues(tb$variable,q_lookup$var,sapply(q_lookup$label,splitF))
  
  tb
})
)

pal_div<-RColorBrewer::brewer.pal(7,"RdBu")

ggplot(corr_list,
       aes(x=variable,y=hap_var,fill=rr))+geom_tile(colour="grey50")+
  theme(axis.text.x = element_text(angle=90),
        panel.grid=element_blank(),
        panel.background = element_blank(),
        axis.ticks=element_blank())+
  scale_fill_gradient2(low=pal_div[length(pal_div)],high=pal_div[1],midpoint=1,name="Relative risk\n(Children unhappy with row\nare x times more\nlikely to think\ncolumn is important)")+
  ylab("Children are unhappy with...")+xlab("Children think x is important...")


```

```{r, fig.width=10}
hap_col<-names(df)[grepl("id|any_(pos|neg|bored)|important_|wt",names(df))]

df_imp<-df[,..hap_col]

hap_cols<-hap_col[grepl("any_(pos|neg|bored)",hap_col)]

imp_cols<-hap_col[grepl("imp",hap_col) & !grepl("dont|wt|Other",hap_col)]


corr_list<-rbindlist(lapply(hap_cols,function(x){
  
  col<-c("id",x,imp_cols,"wt")
  
  tb<-melt(df_imp[,..col
         ],id.vars=c("id",x,"wt"))[,value:=ifelse(value=="Yes",1,0)
                                ][,.(c=sum(wt)),by=.(hap=get(x),variable,value)
                                  ][,perc:=c/sum(c),by=.(variable)
                                    ][hap==1 & value==1]
  
  tb$hap_var<-plyr::mapvalues(x,c("any_pos","any_neg","any_bored"),
                               c("Any positive","Any negative","Any bored"))
  
  tb$variable<-plyr::mapvalues(tb$variable,q_lookup$var,sapply(q_lookup$label,splitF))
  
  tb
})
)

ggplot(corr_list,
       aes(x=variable,y=hap_var,fill=perc*100))+geom_tile(colour="grey50")+geom_text(aes(label=paste0(round(perc,2)*100,"%")))+
  theme(axis.text.x = element_text(angle=90),
        panel.grid=element_blank(),
        panel.background = element_blank(),
        axis.ticks=element_blank())+
  scale_fill_gradient(low=pal[1],high=pal[length(pal)],name="% of respondents saying both")+
  ylab("Children feel...")+xlab("Children think x is important...")

```

```{r}
corr_list<-rbindlist(lapply(hap_cols,function(x){
  
  col<-c("id",x,imp_cols,"wt")
  
  tb<-melt(df_imp[,..col
         ],id.vars=c("id",x,"wt"))[!is.na(get(x)) & !is.na(value)][,value:=ifelse(value=="Yes",1,0)
                                ][,.(c=sum(wt)),by=.(hap=get(x),variable,value)
                                  ][,perc:=c/sum(c),by=.(hap,variable)
                                    ]
  
  tb<-dcast(tb[value==1][,.(variable,perc,hap)],variable~hap,value.var="perc"
            )[,rr:=`1`/`0`][,.(variable,rr)]
  
  
   tb$hap_var<-plyr::mapvalues(x,c("any_pos","any_neg","any_bored"),
                               c("Any positive","Any negative","Any bored"))
  
  tb$variable<-plyr::mapvalues(tb$variable,q_lookup$var,sapply(q_lookup$label,splitF))
  
  
  tb
})
)

pal_div<-RColorBrewer::brewer.pal(7,"RdBu")

ggplot(corr_list,
       aes(x=variable,y=hap_var,fill=rr))+geom_tile(colour="grey50")+
  theme(axis.text.x = element_text(angle=90),
        panel.grid=element_blank(),
        panel.background = element_blank(),
        axis.ticks=element_blank())+
  scale_fill_gradient2(low=pal_div[length(pal_div)],high=pal_div[1],midpoint=1,name="Relative risk\n(Children unhappy with row\nare x times more\nlikely to feel\ncolumn)")+
  ylab("Children are unhappy with...")+xlab("Children feel...")
```

