---
params:
  section: "abc"
  pg: "abc"
  var: "abc"
title: "`r paste0(params$section,': ',params$pg)`"
output: 
 html_document: 
   self_contained: no
   mathjax: null
   highlight: null
   fig_width: 10
   theme: null
   template: "../../CCO_template_html.html"
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = F, warning=F,message = F) # set chunk options
```

<link rel="stylesheet" href="../../styles.css" type="text/css" />


```{r, child='W:/CCO-WORKING-FS/Projects/big ask survey/analysis/markdown/child docs/navigation_child_doc.rmd'}

# add navigation breadcrumbs

```

<script src="extra_js.js"></script>

```{r, include=F}

## add dummy table. Note this isn't shown (include=F) but is required (due to a weird Rmarkdown quirk) to attach javascript libraries to the page

hap_col<-names(df)[grepl("^id$|happy.*_clean|^wt$",names(df))] # select columns to create overall rates chart

df_any_mh<-table_f("any_mh")

two_way_tb_f(df_any_mh,"any_mh","Receiving support from a healthcare worker vs Not",col1)

```



```{r,results='asis'}

## Add HTML picker to page - this chooses what table is visible

if(seg){

  suffix<-"_seg"
}else{
  suffix<-""
}


if(is.null(age_grp)){
cat(paste0('
    
<div class="picker-group">
<label>Select characteristic</label>
<select id="disad_picker',suffix,'">
<option value="sen',suffix,'">SEN</option>
<option value="kinship',suffix,'">Kinship care</option>
<option value="sw',suffix,'">Children in care/with a social worker</option>
<option value="mh',suffix,'">Children receiving mental health support</option>
<option value="yc',suffix,'">Young carers</option>
<option value="yot',suffix,'">Children receiving support from a YOT</option>
</select>
<button class="picker_button" onclick="picker_f(',"'","disad_picker",suffix,"',","'","disad",suffix,"'",')">Go</button>
</div>
    
    
    '))
}else{
  cat(paste0('
    
<div class="picker-group">
<label>Select characteristic</label>
<select id="disad_picker',suffix,'">
<option value="sen',suffix,'">SEN</option>
<option value="kinship',suffix,'">Kinship care</option>
<option value="sw',suffix,'">Children in care/with a social worker</option>
<option value="mh',suffix,'">Children receiving mental health support</option>
<option value="yc',suffix,'">Young carers</option>
<option value="yot',suffix,'">Children receiving support from a YOT</option>
</select>
<button class="picker_button" onclick="picker_f(',"'","disad_picker",suffix,"',","'","disad",suffix,"'",')">Go</button>
</div>
    
    
    '))
}

```

*Please select characteristic of interest and press Go*


```{r, results='asis'}

# create html div as container for table(s) this is what s hidden/shown

  cat(
    paste0('<div id="sen',suffix,'" class="sect disad',suffix,'">\n'
             )
  )


```

**Children with Special Educational Needs (SEN)**

```{r, results='asis'}

#Note all subsequent chunks follow the same pattern as below so annotations not repeated.

if(!seg){

  # If not part of segmentation page calculate SEN variable
  
if(is.null(age_grp)){
df$dem_sen<-with(df,
             ifelse(dfe_phase %in% "Special",
                    "SEN",
                    ifelse(`dem_support_A teaching assistant or SENCO at school` %in% "Yes","SEN",
                           ifelse(grepl("easy",survey),"SEN","Not SEN"))))
             
             df$dem_sen_2<-with(df,
             ifelse(dfe_phase %in% "Special",
                    "SEN",
                    ifelse(`dem_support_A teaching assistant or SENCO at school` %in% "Yes","SEN","Not SEN")))
             
             

}else if(age_grp=="6-8"){
  df$dem_sen<-with(df,
             ifelse(dfe_phase %in% "Special",
                    "SEN",
                    ifelse(`dem_support_A teaching assistant at school` %in% "Yes","SEN",
                           ifelse(grepl("easy",survey),"SEN","Not SEN")))
)
  
}
}

if(is.null(age_grp)){
  
  # If 9-17 yr old data run function to make tables for different age groups - stored in markdown_functions.R script
  # create_age_picker_f - creates tables
  
 create_age_picker_f("_sen","dem_sen","Any SEN vs Not") 
  
}else{
  
  # If 6-8 make table as per child_chars document
  
  df_sen<-table_f("dem_sen")
  
  two_way_tb_f(df_sen,"dem_sen","Any SEN vs Not",col1)
}

# Add definition of SEN variable

cat("\n*Children with SEN defined as those receiving support from a teaching assistant/SENCO, those enrolled in a special school or those completing the easy read version of the questionnaires*\n")

```

</div>

```{r, results='asis'}

  cat(
    paste0('<div id="kinship',suffix,'" class="sect disad',suffix,'">\n'
             )
  )


```

**Children living with relatives other than their parents (in kinship care)**

```{r, results='asis'}

if(!seg){
df<-df[,kinship:=ifelse(is.na(kinship),NA,
                        ifelse(kinship=="Yes","Kinship care","Any other family type"))]
}

if(is.null(age_grp)){

 create_age_picker_f("_kinship","kinship","Living with relatives vs Not")
  
}else{
  df_sen<-table_f("kinship")

two_way_tb_f(df_sen,"kinship","Living with relatives vs Not",col1)

}

cat("\n*Children in kinship care defined as those living with relatives other than their parents*\n")

```

</div>

```{r, results='asis'}

  cat(
    paste0('<div id="sw',suffix,'" class="sect disad',suffix,'">\n'
             )
  )


```

**Children in care or with a social worker**

```{r, results='asis'}
if(!seg){

df$sw<-with(df,ifelse(`dem_support_A social worker`=="Yes" | care=="Yes",
                      "In care/has a social worker","Not in care/has a social worker")
)

df<-df[,sw:=factor(sw,levels=c("Not in care/has a social worker","In care/has a social worker"))]
}

if(is.null(age_grp)){

 create_age_picker_f("_sw","sw","In care/has a social worker vs Not")
  
  cat("\n*Children with a social worker defined as those reporting receiving support from a social worker. Those in care defined by those reporting living with foster parents, in a children's home (secure and non-secure) or those in independent or semi-independent  accommodation supported by the local council*\n")
  
}else{

df_sw<-table_f("sw")

print(two_way_tb_f(df_sw,"sw","In care/has a social worker vs Not",col1))

cat("\n*Children with a social worker defined as those reporting receiving support from a social worker. Those in care defined by those reporting living with foster parents or in a children's home*\n")
}



```

**Children with a social worker only**

```{r, results='asis'}
if(!seg){

df$sw_only<-with(df,ifelse(`dem_support_A social worker`=="Yes" ,
                      "Has a social worker","Does not have a social worker")
)

df<-df[,sw_only:=factor(sw_only,levels=c("Does not have a social worker","Has a social worker"))]
}

if(is.null(age_grp)){

 create_age_picker_f("_swOnly","sw_only","Has a social worker vs Not")
  
}else{

df_sw<-table_f("sw_only")

two_way_tb_f(df_sw,"sw_only","Has a social worker vs Not",col1)
}
```


**Children in care only**

```{r, results='asis'}
if(!seg){
df<-df[,care:=ifelse(is.na(care),NA,
                     ifelse(care=="Yes","In care","Not in care"))][,care:=factor(care,levels=c("Not in care","In care"))]
}

if(is.null(age_grp)){

 create_age_picker_f("_care","care","In care vs Not")
  
}else{
df_care<-table_f("care")

two_way_tb_f(df_care,"care","In care vs Not",col1)
}
```

</div>



```{r, results='asis'}
cat(
    paste0('<div id="mh',suffix,'" class="sect disad',suffix,'">\n'
             )
  )
```

**Children receiving mental health support**

```{r, results='asis'}

if(is.null(age_grp)){

 if(!seg){ 
  
df<-df[,any_mh:=ifelse(is.na(any_mh),NA,ifelse(any_mh=="Yes","Receiving mental health support","Not receiving mental health support"))][,any_mh:=factor(any_mh,levels=c("Not receiving mental health support","Receiving mental health support"))]
}

cat("**Children currently receiving mental health support**\n")

create_age_picker_f("_mh","any_mh","Receiving mental health support vs Not")

cat("\n*Children receiving mental health support are defined as those reporting receiving support from a counsellor therapist or other health care worker and those reporting living in a mental health hospital*\n")

}else{
  
  df_any_mh<-table_f("any_mh")[,any_mh:=ifelse(any_mh=="Yes","Receiving support from a healthcare worker","Not receiving support from a healthcare worker")][,any_mh:=factor(any_mh,levels=c("Not receiving support from a healthcare worker","Receiving support from a healthcare worker"))]

print(two_way_tb_f(df_any_mh,"any_mh","Receiving support from a healthcare worker vs Not",col1))

cat("\n*Children receiving mental health support are defined as those reporting receiving support from a health care worker*\n")

}



```

```{r, results='asis'}
if(is.null(age_grp)){
cat("\n**Children in mental health hospitals**\n")
}

```


```{r, results='asis'}
if(is.null(age_grp)){

  if(!seg){
  
  df<-df[,mh_hospital:=ifelse(is.na(mh_hospital),NA,ifelse(mh_hospital=="Yes","In MH hospital","Not in MH hospital"))][,mh_hospital:=factor(mh_hospital,levels=c("Not in MH hospital","In MH hospital"))]
  }

create_age_picker_f("_mhhosp","mh_hospital","In MH hospital vs Not")

cat("\n*Children in mental health hospitals defined as those reporting living in a mental health hospital*\n")

}



```

</div>

```{r, results='asis'}
cat(
    paste0('<div id="yc',suffix,'" class="sect disad',suffix,'">\n'
             )
  )
```

**Young carers**

```{r, results='asis'}
if(!seg){

df<-df[,yc:=ifelse(`dem_support_A young carers project`=="Yes","Young carer","Not young carer")]

}

if(is.null(age_grp)){
  
  create_age_picker_f("_yc","yc","Young carer vs Not")
}else{

  df_yc<-table_f("yc")[!is.na(yc)]

  
two_way_tb_f(df_yc,"yc","Young carer vs Not",col1)
}

cat("\n*Young carers defined as children reporting receiving support from a young carers' project*\n")

```

</div>

```{r, results='asis'}

cat(
  paste0('<div id="yot',suffix,'" class="sect disad',suffix,'">\n'
             )
  )

```

**Children receiving support from Youth Offending Teams (YOTs)**

```{r, results='asis'}

if(!seg){

df<-df[,yot:=ifelse(`dem_support_A youth offending team`=="Yes","Receiving support from YOT","Not receiving support from YOT")]

}

if(is.null(age_grp)){
  
  create_age_picker_f("_yot","yot","Receiving support from YOT vs Not")
}else{

  cat("\n*Data unavailable for children aged 6-8 as they are too young to be arrested or charged with a crime*\n")
}

cat("\n*Defined as children who report receiving support from a Youth Offending Team (YOT)*\n")


```

</div>
