---
params:
  section: "abc"
  pg: "abc"
  var: "abc"
title: "What proportion of children are happy with their life at the moment?"
output: 
 html_document: 
   self_contained: no
   mathjax: null
   highlight: null
   fig_width: 10
   theme: null
   template: "../../CCO_template_html.html"
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = F, warning=F,message = F) # set chunk options
```

<link rel="stylesheet" href="../../styles.css" type="text/css" />

```{r, child='W:/CCO-WORKING-FS/Projects/big ask survey/analysis/markdown/child docs/Copies for analysis/navigation_child_doc_phappy.rmd'}

# read in breadcrumbs. HTML below creates key stat boxes

```

<script src="extra_js.js"></script>

### About this data

Children aged 9-17 were asked “How happy are you with these things in your life now?”, and were given a list of items to assess with the response options ‘Very Unhappy’, ‘Unhappy’, ‘Neither happy nor unhappy’, ‘Happy’ or ‘Very Happy’. The list of items was:

* My friendships
* My experiences online
* My personal safety
* My access to somewhere outside to go to have fun
* The choice of things to do in my local area
* Life at school
* My progress in education
* My mental health
* My physical health
* My family’s health
* My family life
* My family’s ability to buy things we need
* My life overall

The tables below show the percentage of children *happy* or *very happy* with various aspects of their lives broken down by characteristics including age, gender, ethnicity and disadvantage (e.g. children in care and special educational needs).


</br>

### Overall results

```{r overall, echo=FALSE}

require(data.table)
require(dplyr)
require(tidyr)
require(knitr)
require(kableExtra)
require(downloadthis)

### Overall ###

overall_table <- fread("W:/CCO-WORKING-FS/Projects/big ask survey/analysis/aux data/perc happy/phappy_overall.csv")

kable(overall_table) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) 

# overall_table %>% 
#   download_this(
#     output_name = "big ask data download",
#     output_extension = ".csv",
#     button_label = "Download data as csv",
#     button_type = "default",
#     has_icon = TRUE,
#     icon = "fa fa-save"
#   )

```

<br/>


### Age


```{r age, echo=FALSE}


### Age groups ###

age_table <- fread("W:/CCO-WORKING-FS/Projects/big ask survey/analysis/aux data/perc happy/phappy_age.csv")

kable(age_table) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

# age_table %>% 
#   download_this(
#     output_name = "big ask data download",
#     output_extension = ".csv",
#     button_label = "Download data as csv",
#     button_type = "default",
#     has_icon = TRUE,
#     icon = "fa fa-save"
#   )

```


<br/>

### Gender

```{r gender, echo=FALSE}

gender_table <- fread("W:/CCO-WORKING-FS/Projects/big ask survey/analysis/aux data/perc happy/phappy_gender.csv")

kable(gender_table) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

# gender_table %>% 
#   download_this(
#     output_name = "big ask data download",
#     output_extension = ".csv",
#     button_label = "Download data as csv",
#     button_type = "default",
#     has_icon = TRUE,
#     icon = "fa fa-save"
#   )

```

<br/>

### Ethnicity

```{r ethnicity, echo=FALSE}

ethnicity_table <- fread("W:/CCO-WORKING-FS/Projects/big ask survey/analysis/aux data/perc happy/phappy_ethnicity.csv")

kable(ethnicity_table) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

# ethnicity_table %>% 
#   download_this(
#     output_name = "big ask data download",
#     output_extension = ".csv",
#     button_label = "Download data as csv",
#     button_type = "default",
#     has_icon = TRUE,
#     icon = "fa fa-save"
#   )

```

<br/>

### Detailed ethnicity

```{r dethnicity, echo=FALSE}

dethnicity_table <- fread("W:/CCO-WORKING-FS/Projects/big ask survey/analysis/aux data/perc happy/phappy_dethnicity.csv")

kable(dethnicity_table) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

# dethnicity_table %>% 
#   download_this(
#     output_name = "big ask data download",
#     output_extension = ".csv",
#     button_label = "Download data as csv",
#     button_type = "default",
#     has_icon = TRUE,
#     icon = "fa fa-save"
#   )


```

<br/>

### Income deprivation affecting children index (IDACI) decile

```{r idaci, echo=FALSE}

idaci_table <- fread("W:/CCO-WORKING-FS/Projects/big ask survey/analysis/aux data/perc happy/phappy_idaci.csv")

kable(idaci_table) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

# idaci_table %>% 
#   download_this(
#     output_name = "big ask data download",
#     output_extension = ".csv",
#     button_label = "Download data as csv",
#     button_type = "default",
#     has_icon = TRUE,
#     icon = "fa fa-save"
#   )

```

<br/>

### Children in foster care or with a social worker

```{r care or sw, echo=FALSE}

caresw_table <- fread("W:/CCO-WORKING-FS/Projects/big ask survey/analysis/aux data/perc happy/phappy_caresw.csv")

kable(caresw_table) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

# caresw_table %>% 
#   download_this(
#     output_name = "big ask data download",
#     output_extension = ".csv",
#     button_label = "Download data as csv",
#     button_type = "default",
#     has_icon = TRUE,
#     icon = "fa fa-save"
#   )

```

<br/>

### Children in foster care only

```{r care only, echo=FALSE}

care_table <- fread("W:/CCO-WORKING-FS/Projects/big ask survey/analysis/aux data/perc happy/phappy_care.csv")

kable(care_table) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

# care_table %>% 
#   download_this(
#     output_name = "big ask data download",
#     output_extension = ".csv",
#     button_label = "Download data as csv",
#     button_type = "default",
#     has_icon = TRUE,
#     icon = "fa fa-save"
#   )

```

<br/>

### Children with a social worker only

```{r sw only, echo=FALSE}

sw_table <- fread("W:/CCO-WORKING-FS/Projects/big ask survey/analysis/aux data/perc happy/phappy_sw.csv")

kable(sw_table) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

# sw_table %>% 
#   download_this(
#     output_name = "big ask data download",
#     output_extension = ".csv",
#     button_label = "Download data as csv",
#     button_type = "default",
#     has_icon = TRUE,
#     icon = "fa fa-save"
#   )

```

<br/>

### Children with special educational needs (SEN)

```{r sen, echo=FALSE}

sen_table <- fread("W:/CCO-WORKING-FS/Projects/big ask survey/analysis/aux data/perc happy/phappy_sen.csv")

kable(sen_table) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

# sen_table %>% 
#   download_this(
#     output_name = "big ask data download",
#     output_extension = ".csv",
#     button_label = "Download data as csv",
#     button_type = "default",
#     has_icon = TRUE,
#     icon = "fa fa-save"
#   )

```

<br/>

### Children receiving mental health support

```{r mh, echo=FALSE}

mh_table <- fread("W:/CCO-WORKING-FS/Projects/big ask survey/analysis/aux data/perc happy/phappy_mh.csv")

kable(mh_table) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

# mh_table %>% 
#   download_this(
#     output_name = "big ask data download",
#     output_extension = ".csv",
#     button_label = "Download data as csv",
#     button_type = "default",
#     has_icon = TRUE,
#     icon = "fa fa-save"
#   )

```

<br/>

### Young carers

```{r carers, echo=FALSE}

yc_table <- fread("W:/CCO-WORKING-FS/Projects/big ask survey/analysis/aux data/perc happy/phappy_youngcarers.csv")

kable(yc_table) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

# yc_table %>% 
#   download_this(
#     output_name = "big ask data download",
#     output_extension = ".csv",
#     button_label = "Download data as csv",
#     button_type = "default",
#     has_icon = TRUE,
#     icon = "fa fa-save"
#   )

```

<br/>

### Children receiving support from Youth Offending Teams (YOTs)

```{r yot, echo=FALSE}

yot_table <- fread("W:/CCO-WORKING-FS/Projects/big ask survey/analysis/aux data/perc happy/phappy_yot.csv")

kable(yot_table) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

# yot_table %>% 
#   download_this(
#     output_name = "big ask data download",
#     output_extension = ".csv",
#     button_label = "Download data as csv",
#     button_type = "default",
#     has_icon = TRUE,
#     icon = "fa fa-save"
#   )

```

<br/>

### Children in kinship care

```{r kinship, echo=FALSE}

kinship_table <- fread("W:/CCO-WORKING-FS/Projects/big ask survey/analysis/aux data/perc happy/phappy_kinship.csv")

kable(kinship_table) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

# kinship_table %>% 
#   download_this(
#     output_name = "big ask data download",
#     output_extension = ".csv",
#     button_label = "Download data as csv",
#     button_type = "default",
#     has_icon = TRUE,
#     icon = "fa fa-save"
#   )

```

