---
params:
  section: "abc"
  pg: "abc"
  var: "abc"
title: "`r paste0(params$section,': ',params$pg)`"
output: 
 html_document: 
   self_contained: no
   mathjax: null
   highlight: null
   fig_width: 10
   theme: null
   template: "../../CCO_template_html.html"
---

```{r setup, include=FALSE}
knitr::knit_hooks$set(optipng = knitr::hook_optipng)

knitr::opts_chunk$set(echo = F, warning=F,message = F)

require(readxl)
require(data.table)
require(dplyr)
require(ggplot2)
require(reactable)
require(htmltools)
require(tippy)

stem<-"W:/CCO-WORKING-FS/Projects/big ask survey/analysis/survey data/cleaned data/"

search_str<-"happy.*clean"

dk_vals<-c("I don't know","Not applicable","dont know","I dont want to say","Other")

target_vals<-c("Unhappy","Very unhappy","sad","unhappy")


table_f<-function(x,df_use=df){
  
  x<-unlist(strsplit(x,"[|]"))
  
  reg<-paste0("^",x,"$")
  
  reg_string<-paste0("^id$|happy.*clean|wt|",paste0(reg,collapse="|"))
  hap_col<-names(df_use)[grepl(reg_string,names(df_use))]

  
df_la<-melt(df_use[,..hap_col],id.vars = c("id",x,"wt"))[,variable:=plyr::mapvalues(variable,
                                                                                    q_lookup$var,
                                                                                    q_lookup$label)]

df_la[,value:=ifelse(value %in% dk_vals,NA,
                        ifelse(value %in% target_vals,1,0))
           ]
}

source("W:/CCO-WORKING-FS/Projects/big ask survey/analysis/scripts/markdown_functions.R",local=knitr::knit_global())
  
col1<-"% of children unhappy with..."

  
```

<link rel="stylesheet" href="../../styles.css" type="text/css" />

```{r}

df<-readRDS("W:/CCO-WORKING-FS/Projects/big ask survey/analysis/survey data/final data/6-8_weighted.rds")


#imd<-fread(file="W:/CCO-WORKING-FS/Projects/big ask survey/analysis/aux data/imd2019lsoa.csv")[Measurement=="Decile"]

imd<-fread(file="W:/CCO-WORKING-FS/Projects/big ask survey/analysis/aux data/idaci.csv")

df<-df[!dfe_phase %in% "Secondary"
       ][,id:=paste0(id,survey)
         ][,dem_gender_clean:=plyr::mapvalues(dem_gender_clean,
                                              c("Boy","Girl"),c("Male","Female"))
           ][,any_mh:=ifelse(`dem_support_A healthcare worker`=="Yes","Yes","No")]

q_lookup<-fread("W:\\CCO-WORKING-FS\\Projects\\big ask survey\\analysis\\aux data\\6-8_happy_q_lookup.csv")

age_grp<-"6-8"

```

```{r, child='W:/CCO-WORKING-FS/Projects/big ask survey/analysis/markdown/child docs/navigation_child_doc.rmd'}


```

<script src="extra_js.js"></script>


<h3>Key stats</h3>
<div class="stat-boxes">

<div class="col-xs-12 col-sm-6 col-lg-3">
<div class="stat">
<div class="stat-box-outer">
<div class="stat-box-inner">
<p class="figure">Key stat</p>
</div>
</div>
</div>
</div>

<div class="col-xs-12 col-sm-6 col-lg-3">
<div class="stat">
<div class="stat-box-outer">
<div class="stat-box-inner">
<p class="figure">Key stat</p>
</div>
</div>
</div>
</div>

<div class="col-xs-12 col-sm-6 col-lg-3">
<div class="stat">
<div class="stat-box-outer">
<div class="stat-box-inner">
<p class="figure">Key stat</p>
</div>
</div>
</div>
</div>

<div class="col-xs-12 col-sm-6 col-lg-3">
<div class="stat">
<div class="stat-box-outer">
<div class="stat-box-inner">
<p class="figure">Key stat</p>
</div>
</div>
</div>
</div>

</div>

<h3>About this data</h3>

INTRO TEXT

<h3>How do children report feeling most of the time?</h3>

*Note children can select more than one option*

```{r}

 reg_string<-"^id$|feel.*_|wt"
 
 hap_col<-names(df)[grepl(reg_string,names(df))]


df_feel<-melt(df[,..hap_col],id.vars = c("id","wt"))[,variable:=gsub("^.*_","",variable)]

df_feel<-df_feel[,value:=ifelse(value %in% dk_vals,NA,
                        ifelse(value %in% "Yes",1,0))
           ][,any_neg:=ifelse(variable %in% c("Stressed","Lonely","Worried","Sad"),1,0)
             ][,any_pos:=ifelse(variable %in% c("Happy","Safe","Calm","Energetic","Excited"),1,0)
               ][,any_bored:=ifelse(variable=="Bored",1,0)]

df_feel_perc<-df_feel[,.(c=sum(wt)),by=.(variable,value)
        ][,perc:=c/sum(c),by=variable][value==1]

ggplot(df_feel_perc,
       aes(x=reorder(variable,perc),y=perc*100))+
  geom_col(fill="light blue",colour="grey20")+
  geom_text(aes(label=paste0(round(perc,2)*100,"%")),hjust=-0.1)+
  coord_flip()+
  theme_bw()+ylab("% of 6-8 yr olds")+xlab("")

```
<h3>How many aspects of their lives are children unhappy with?</h3>

```{r}

# Copied over 9-17 code, table shows up with zero - Chunk to make table of number of aspects of life children are unhappy with

hap_col<-names(df)[grepl("^id$|happy.*_clean|^wt$",names(df))] # select columns to create overall rates chart

df_happy<-melt(df[,..hap_col],id.vars = c("id","wt")) # convert to long format

# recode outcomes and get number of unhappy items for each person
dat<-copy(df_happy)[,value:=ifelse(value %in% dk_vals,NA,
                        ifelse(value %in% target_vals,1,0))
           ][!is.na(value)
             ][,.(tot=sum(value,na.rm=T)),by=.(id,wt)]

# Work out cumulative percentages by count of unhappiness items
tb<-dat[,.(c=sum(wt)),by=.(tot)
    ][,perc:=c/sum(c)][order(-tot)
                       ][,cum_perc:=cumsum(perc)
                         ][,cum_perc:=round(ifelse(tot==0,perc,cum_perc),3)*100
                           ][,tot:=ifelse(tot==0,"0",ifelse(tot==max(tot),"All",paste0(tot,"+")))
                             ][,.(tot,cum_perc)
                               ]

# create table
names(tb)<-c("Number of aspects of their life children are unhappy with","% of respondents")

div(reactable(tb,
             columns=list(`Number of aspects of their life children are unhappy with`=colDef(),`% of respondents`=colDef()),
    pagination = F,
    fullWidth = T,
    bordered = T,
    resizable = T,
    searchable = F,
    showSortable = T,
    language = reactableLang(searchPlaceholder = "Search table...",searchLabel = "")),
    downloadthis::download_this(tb,output_name ="big_ask_download",output_extension = ".xlsx")
)



```


```{r}

df_sent<-df_feel[value==1][,lapply(.SD,function(x){
  ifelse(sum(x)>0,1,0)
  }),by=.(id,wt),.SDcols=c("any_neg","any_pos","any_bored")]



df_sent_out<-melt(df_sent,id.vars=c("id","wt")
              )[,.(c=sum(wt)),by=.(variable,value)
                ][,perc:=c/sum(c),by=.(variable)][value==1]

ggplot(df_sent_out[,variable:=plyr::mapvalues(variable,c("any_pos","any_neg","any_bored"),
                                          c("Any positive","Any negative","Any bored"))],
       aes(x=reorder(variable,perc),y=perc*100))+
  geom_col(fill="light blue",colour="grey20")+
  geom_text(aes(label=paste0(round(perc,2)*100,"%")),hjust=-0.1)+
  coord_flip()+
  theme_bw()+ylab("% of 6-8 yr olds")+xlab("")


```



<h3>How happy are they about different aspects of their life?</h3>

```{r}
hap_col<-names(df)[grepl("^id$|happy.*_clean|wt",names(df))]

df_happy<-melt(df[,..hap_col],id.vars = c("id","wt"))

#dat<-copy(df_happy)[,value:=ifelse(value %in% dk_vals,NA,
         #               ifelse(value %in% c("Unhappy","Very unhappy","sad","unhappy"),"Sad",
          #                     ifelse(
         #                        value %in% c("neutral","neural"),"Neutral","Happy"
         #                      )))
         #  ][!is.na(value)][,.(c=sum(wt)),by=.(variable,value)][,perc:=round(c/sum(c),3)*100,by=.(variable)][,.(variable,perc,value)]

dat<-copy(df_happy)[,value:=ifelse(value %in% dk_vals,NA,
                        ifelse(value %in% target_vals,"Unhappy",
                               ifelse(value %in% c("Neither happy nor unhappy (neutral)","neural"),"Neutral","Happy")))
           ][!is.na(value)][,.(c=sum(wt)),by=.(variable,value)][,perc:=round(c/sum(c),2)*100,by=.(variable)][,.(variable,perc,value)]

dat<-merge(dat,q_lookup,by.x="variable",by.y="var")

dat_unhap<-unique(dat[value=="Unhappy",.(variable,unhap_perc=perc)])

dat<-merge(dat,dat_unhap,by="variable")

pal_rgb<-c("#57C4AD","#EDA247","#DB4325") # define colours for bar fills


# Create plot
ggplot(dat,
       aes(x=reorder(label,unhap_perc),y=perc,group=value,fill=value))+
  geom_col(colour="grey20",position = position_dodge(0.9))+coord_flip()+geom_text(aes(label=paste0(perc,"%")),hjust=ifelse(dat$perc<10,-0.1,1),position = position_dodge(0.9))+
  scale_fill_manual(values=pal_rgb,name="")+
  theme_bw()+xlab("")+ylab("% of 6-8 yr olds")

```

<h3>How is how they are feeling related to what they are happy with?</h3>

```{r, fig.width=10}

df<-merge(df,df_sent)

hap_col<-names(df)[grepl("id|feel_|happy_.*clean|wt",names(df))]

df_imp<-df[,..hap_col]

hap_cols<-hap_col[grepl("happy",hap_col)]

imp_cols<-hap_col[grepl("feel",hap_col) & !grepl("dont want|wt",hap_col)]



```

*Correlations between how children describe their life and what they are unhappy with*

*Note: red = stronger positive correlation (i.e. children selecting row are more likely to also select column in the chart below), blue = stronger negative correlation*

```{r}
corr_list<-rbindlist(lapply(hap_cols,function(x){
  
  col<-c("id",x,imp_cols,"wt")
  
  tb<-melt(df_imp[,..col
         ],id.vars=c("id",x,"wt"))[,(x):=ifelse(get(x) %in% c("dont know","I dont know"),NA,
                                           ifelse(get(x) %in% c("Unhappy","Very unhappy","sad"),1,0))
                              ][!is.na(get(x)) & !is.na(value)][,value:=ifelse(value=="Yes",1,0)
                                ][,.(c=sum(wt)),by=.(hap=get(x),variable,value)
                                  ][,perc:=c/sum(c),by=.(hap,variable)
                                    ]
  
  tb<-dcast(tb[value==1][,.(variable,perc,hap)],variable~hap,value.var="perc"
            )[,rr:=`1`/`0`][,.(variable,rr)]
  
  
  tb$hap_var<-splitF(q_lookup$label[q_lookup$var==x])
  
  tb$variable<-gsub("^.*_","",tb$variable)
  
  tb
})
)

pal_div<-RColorBrewer::brewer.pal(7,"RdBu")

ggplot(corr_list,
       aes(x=variable,y=hap_var,fill=rr))+geom_tile(colour="grey50")+
  geom_text(aes(label=round(rr,1)))+
  theme(axis.text.x = element_text(angle=90),
        panel.grid=element_blank(),
        panel.background = element_blank(),
        axis.ticks=element_blank())+
  scale_fill_gradient2(low=pal_div[length(pal_div)],high=pal_div[1],midpoint=1,name="Relative risk\n(Children unhappy with row\nare x times more\nlikely to feel\ncolumn)")+
  ylab("Children are unhappy with...")+xlab("Children feel...")

```

*Correlations between how children describe their life and what they are unhappy with*

*Note: red = stronger positive correlation (i.e. children selecting row are more likely to also select column in the chart below), blue = stronger negative correlation*

```{r}
hap_col<-names(df)[grepl("id|any_(pos|neg|bored)|happy_.*clean|wt",names(df))]

df_imp<-df[,..hap_col]

hap_cols<-hap_col[grepl("happy",hap_col)]

imp_cols<-hap_col[grepl("any_(pos|neg|bored)",hap_col) & !grepl("dont want|wt",hap_col)]

corr_list<-rbindlist(lapply(hap_cols,function(x){
  
  col<-c("id",x,imp_cols,"wt")
  
  tb<-melt(df_imp[,..col
         ],id.vars=c("id",x,"wt"))[,(x):=ifelse(get(x) %in% c("dont know","I dont know"),NA,
                                           ifelse(get(x) %in% c("Unhappy","Very unhappy","sad","unhappy"),1,0))
                              ][!is.na(get(x)) & !is.na(value)][,.(c=sum(wt)),by=.(hap=get(x),variable,value)
                                  ][,perc:=c/sum(c),by=.(hap,variable)
                                    ]
  
  tb<-dcast(tb[value==1][,.(variable,perc,hap)],variable~hap,value.var="perc"
            )[,rr:=`1`/`0`][,.(variable,rr)]
  
  
  tb$hap_var<-splitF(q_lookup$label[q_lookup$var==x])
  
  tb$variable<-plyr::mapvalues(tb$variable,c("any_pos","any_neg","any_bored"),
                               c("Any positive","Any negative","Any bored"))
  
  
  tb
})
)

pal_div<-RColorBrewer::brewer.pal(7,"RdBu")

ggplot(corr_list,
       aes(x=variable,y=hap_var,fill=rr))+geom_tile(colour="grey50")+
  geom_text(aes(label=round(rr,1)))+
  theme(axis.text.x = element_text(angle=90),
        panel.grid=element_blank(),
        panel.background = element_blank(),
        axis.ticks=element_blank())+
  scale_fill_gradient2(low=pal_div[length(pal_div)],high=pal_div[1],midpoint=1,name="Relative risk\n(Children unhappy with row\nare x times more\nlikely to feel\ncolumn)")+
  ylab("Children are unhappy with...")+xlab("Children feel...")

```

```{r}

```