---
title: "The Big Ask Survey: Results"
output: 
 html_document: 
   self_contained: no
   theme: null
   mathjax: null
   highlight: null
   css: styles.css
   template: "CCO_template_html.html"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
```



```{r}

#<link rel="stylesheet" href="../../styles.css" type="text/css" />

```
<h2>Introduction</h2>

INTRO TEXT

<h2>9-17 year olds</h2>

<div class="topic_navList">
<a class="meta_navList_link" href="9-17_happy/pages/9-17_happy_index.html">
<h3 class="list_header">How happy are children with their life currently?</h3></a>
</div>

<div class="topic_navList">
<a class="meta_navList_link" href="9-17_important/pages/9-17_important_index.html">
<h3 class="list_header">What do children think is important for their future?</h3></a>
</div>

<div class="topic_navList">
<a class="meta_navList_link" href="9-17_worry/pages/9-17_worry_index.html">
<h3 class="list_header">What do children worry about having in the future?</h3></a>
</div>

<div class="topic_navList">
<a class="meta_navList_link" href="9-17_parents/pages/9-17_parents_index.html">
<h3 class="list_header">Do children think they will have a better life than their parents?</h3></a>
</div>

<h2>6-8 year olds</h2>

<div class="topic_navList">
<a class="meta_navList_link" href="6-8_happy/pages/6-8_happy_index.html">
<h3 class="list_header">How happy are children with their life currently?</h3></a>
</div>

<div class="topic_navList">
<a class="meta_navList_link" href="6-8_important/pages/6-8_important_index.html">
<h3 class="list_header">What do children think is important for their future?</h3></a>
</div>

<h2>Children in youth custody</h2>

<div class="topic_navList">
<a class="meta_navList_link" href="YOI data/pages/yoi.html">
<h3 class="list_header">Children in youth custody</h3></a>
</div>